
\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Said Altan} \\ \vspace{1pt}
   
\end{center}

\begin{center}

    \small 343-988-3084 $|$ \href{mailto:x@x.com}{\underline{altansaid13@outlook.com}} $|$ 
    \href{https://linkedin.com/in/altansaid}{\underline{linkedin.com/in/altansaid}} $|$
    \href{https://github.com/altansaid}{\underline{github.com/altansaid}}
\end{center}




%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{Jul 2025 -- Present}
      {Arbitrage Cyclops}{Toronto, ON}
      \resumeItemListStart
       \resumeItem{Built and optimized a \textbf{React + Redux} dashboard handling \textbf{10M+ product records}, improving large-dataset filtering and pagination performance across arbitrage views.}
        \resumeItem{Led incremental \textbf{TypeScript} adoption across shared UI components and state slices, reducing runtime errors and improving code review reliability.}
        \resumeItem{Optimized Firestore queries with indexing, debounced search, and memoized selectors to reduce unnecessary re-renders and improve responsiveness for large result sets.}
        \resumeItem{Integrated React views with \textbf{REST} endpoints and Node.js services, and contributed to deploying static assets through \textbf{AWS} (S3/CloudFront) for more reliable delivery.}
       
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Web Developer Intern}{Sep 2024 -- Dec 2024}
      {Solace}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed and maintained production web interfaces using \textbf{JavaScript}, \textbf{HTML/CSS}, and React by shipping reusable UI components and managing component lifecycle-driven interactions, ensuring consistent behavior across content-heavy, high-traffic pages in a live environment.}

\resumeItem{Redesigned a complex scroll-based Table of Contents and navigation system by implementing state-driven active section management in JavaScript, resolving edge cases such as duplicate open/close events, incorrect section activation, and offset rendering issues during rapid scroll and click interactions.}

\resumeItem{Designed and built a platform hosted on a company subdomain for a company-wide initiative, translating \textbf{Figma} designs into a modular, component-driven frontend with responsive \textbf{HTML/CSS}, contributing to a platform redesign that supported a \textbf{50\%} year-over-year increase in traffic.}

\resumeItem{Collaborated with engineers to diagnose and resolve critical production build and deployment issues on a \textbf{Gatsby/React} platform, addressing \textbf{Node.js} and framework version incompatibilities to restore reliable builds and deployment stability.}

\resumeItem{Ensured responsive layouts, cross-browser compatibility, and basic accessibility considerations using semantic HTML
and consistent component structure.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{\href{https://www.rolevanta.com}{Rolevanta}} $|$ \emph{Next.js, Python, FastAPI}}{}
          \resumeItemListStart
        \resumeItem{Architected and shipped a production-grade career application system featuring a \textbf{4-stage LLM orchestration} pipeline (JD analysis → content strategy → section drafting → ATS scoring) that converts unstructured resume data into role-specific, structured outputs.}
        \resumeItem{Designed and implemented a scalable full-stack architecture with \textbf{FastAPI, Next.js App Router}, Supabase, and PostgreSQL, including SSR authentication, tier-based access control, async request handling, versioned data models, and secure Stripe payment processing.}
        \resumeItem{Established production reliability and platform integrity through \textbf{600+ automated tests} (unit, integration, E2E), CI enforcement via GitHub Actions, zero-downtime schema migrations, rate limiting, input sanitization against prompt injection, and end-to-end security hardening.}
          \resumeItemListEnd





    
      \resumeProjectHeading
          {\textbf{\href{https://plab2practice.com}{PLAB2 Practice Platform}} $|$ \emph{React, TypeScript, REST APIs, PostgreSQL}}{\href{https://github.com/altansaid/plab2projectnew}{Github}}
          \resumeItemListStart
            \resumeItem{Built a React + TypeScript SPA supporting Doctor/Patient/Observer roles and time-boxed consultation flows, enabling real-time session handling for hundreds of concurrent users.}
        \resumeItem{Designed responsive, WCAG-aware UI components with Tailwind CSS and Material UI, ensuring clear layouts, keyboard-friendly navigation, and consistent behavior across breakpoints.}
        \resumeItem{Integrated \textbf{REST} APIs and WebSocket (STOMP) endpoints from a Spring Boot backend to keep session state synchronized in under \textbf{200ms} on typical connections.}
   
          \resumeItemListEnd

    \resumeSubHeadingListEnd



%
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Algonquin College of Applied Arts and Technology}{Ottawa, ON}
      {Web Development and Internet Applications}{Sep 2023 -- April 2025}
    
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Frontend}{: React, Next.js, TypeScript, Redux, Tailwind CSS} \\
     \textbf{Backend}{: Node.js, FastAPI, Spring Boot, REST APIs, WebSockets} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, MySQL} \\
     \textbf{Cloud \& DevOps:}{: AWS, GCP, Docker, GitHub Actions}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
