\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{times}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}

\begin{document}

\begin{flushright}
Muhammed Said Altan\\[0.3em]
altansaid13@outlook.com\\[0.3em]
LinkedIn: linkedin.com/in/saidaltan\\[0.3em]
Ottawa, ON, Canada
\end{flushright}

\vspace{1em}

\begin{flushleft}
\today
\end{flushleft}

\vspace{1em}

Dear Hiring Manager,

The opportunity to join Premier Construction Software as a Junior Full Stack Developer is quite compelling, especially because of your innovative approach to streamlining construction management. Having had hands-on experience in developing scalable web solutions, I am excited about using my skills to enhance your team’s efficiency and contribute to your platform's growth.

During my internship at Solace, I honed my abilities in both frontend and backend development, working with JavaScript, PHP, and Node.js to enhance product features and reliability. I tackled real-world challenges like optimizing CI/CD pipelines and integrating RESTful services, which significantly reduced deployment failures. This experience, combined with a strong foundation in SQL from my projects, aligns well with your need for rigorous backend work using C# and the .NET framework.

Moreover, my project work on the PLAB2 Practice Platform has provided me with a solid understanding of building secure, real-time applications, utilizing technologies such as React and TypeScript. This directly complements your emphasis on full-stack proficiency, particularly with Angular and cloud-based environments. I’ve actively participated in Agile sprints, refining my skills in sprint planning and collaborative problem-solving, which I am eager to bring to your development processes.

I am genuinely enthused about the possibility of contributing to Premier Construction Software, leveraging modern tools and practices to tackle the industry's challenges. Let’s discuss how my approach and experiences can seamlessly integrate with your team.

Sincerely,\\[2em]
Muhammed Said Altan

\end{document}