\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Decreased bounce rate by \textbf{42\%} by deploying reusable \textbf{JavaScript}/\textbf{jQuery} Table of Contents across enterprise docs to improve cross-page navigation.}
        \resumeItem{Optimized accessibility and \textbf{SEO} across \textbf{React} sites, raising Lighthouse scores to \textbf{90+} using semantic markup and \textbf{Node.js} with \textbf{Bootstrap}.}
        \resumeItem{Boosted engagement by \textbf{50\%} by building an internal microsite with modular content blocks using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}.}
        \resumeItem{Resolved environment mismatches in \textbf{Node.js} pipelines, reducing \textbf{CI/CD} deployment failures by \textbf{80\%} and accelerating production readiness.}
        \resumeItem{Created cross-platform mockups with \textbf{Figma}, \textbf{Photoshop}, and \textbf{Illustrator}, promoting consistent UI delivery across global \textbf{Agile} teams.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Served \textbf{500+ users} by building real-time practice platform with scalable \textbf{React} frontend and \textbf{Spring Boot} backend using \textbf{WebSockets}.}
        \resumeItem{Reduced latency to under \textbf{200ms} with efficient \textbf{WebSocket}/\textbf{STOMP} pipeline for synchronized roles, feedback, and timers.}
        \resumeItem{Implemented secure role-based authentication using \textbf{JWT}, \textbf{Spring Security}, and over \textbf{60+ REST APIs}.}
        \resumeItem{Enhanced performance using \textbf{PostgreSQL}, \textbf{Docker}, and automated deployment via \textbf{Render} and \textbf{Vercel}.}
        \resumeItem{Designed WCAG-compliant frontend in \textbf{React} and \textbf{TailwindCSS} with dynamic cases and automatic session logging.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Generated dynamic interview questions using \textbf{Gemini API} on full-stack \textbf{React}/\textbf{Node.js} app with role-based login system.}
        \resumeItem{Improved security using \textbf{JWT}, \textbf{Google OAuth}, bcrypt hashing, and timed token-based email recovery.}
        \resumeItem{Built note-pinning and tracking workflows backed by a scalable \textbf{MongoDB} document store for personalized prep.}
        \resumeItem{Enabled encrypted uploads with image embedding using \textbf{Multer} middleware and secure asset handling.}
        \resumeItem{Improved UI responsiveness using \textbf{TailwindCSS} and \textbf{Framer Motion}, deployed via containerized \textbf{Vercel} \textbf{CI/CD} pipelines.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Restaurant Review Management System}}{\href{https://github.com/altansaid/restaurantreviewmanagementsystem}{GitHub}}{Full-Stack Review App}{}
      \resumeItemListStart
        \resumeItem{Built modular \textbf{ASP.NET Core MVC} backend with \textbf{React} frontend supporting dynamic review forms and client-side validation.}
        \resumeItem{Implemented structured error handling in \textbf{C\#} middleware with \textbf{Bootstrap 5}, increasing form reliability.}
        \resumeItem{Secured review workflows with session-based authentication and server-side logic for consistent experience across sessions.}
        \resumeItem{Improved filter and sort speeds by optimizing SQL queries via \textbf{.NET LINQ} and indexed fields.}
        \resumeItem{Delivered mobile-responsive UI with field-level validation and clean layout using \textbf{Bootstrap} styling.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}