\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 

\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com/?utm_source=sep9}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{Sep 2023 -- Apr 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(HTML, CSS, React), UI/UX Design, Object-Oriented Programming(JavaScript, C\#) Software Development Lifecycle, Algorithms for Computer Science, Network OS(Linux)} 
  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Enhanced navigation efficiency and reduced bounce rates by \textbf{42\%} through the development and deployment of a reusable \textbf{JavaScript/jQuery} Table of Contents plugin, integrating accessible and scalable UI design.}
\resumeItem{Improved CI/CD pipeline reliability by \textbf{80\%} by resolving \textbf{Node.js} environment mismatches, ensuring seamless deployment and build processes.}
\resumeItem{Boosted employee engagement by \textbf{50\%} with an internal microsite built using \textbf{PHP, REST APIs, and Bootstrap}, which allowed secure and modular content handling across departments.}
\resumeItem{Enhanced scalable and secure application development by integrating \textbf{RESTful services}, optimizing modular components for both front-end and back-end operations.}
\resumeItem{Supported Agile work culture by collaborating in global \textbf{Agile sprints}, focusing on documentation, maintainability, and cross-functional delivery through effective backlog grooming and peer reviews.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Real-Time Medical Exam Practice Platform}}
{\href{\detokenize{https://plab2practice.com/?utm_source=sep9&utm_medium=resume}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}

\resumeItemListStart
\resumeItem{Engineered a scalable platform employing \textbf{React}, \textbf{TypeScript}, and \textbf{WebSockets} supporting over \textbf{500+ active users} for synchronized, multi-user collaboration in medical exam practice.}
\resumeItem{Established modular \textbf{Spring Boot microservices} with \textbf{JWT authentication}, ensuring secure, role-based practice sessions aligned with maintainability standards.}
\resumeItem{Created modern, WCAG-compliant UI using Material-UI and Tailwind CSS, delivering consistent cross-device performance tailored for public-sector accessibility needs.}
\resumeItem{Formulated solutions for \textbf{high-concurrency workloads} via Dockerized deployments and CI/CD-ready configs, facilitating reliable cloud-deployed digital training modernization.}
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Interview Preparation App}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
\resumeItem{Developed a scalable \textbf{full-stack platform} utilizing \textbf{React} and \textbf{Node.js/Express} with MongoDB, integrating \textbf{AI-driven} interview question generation via Google's Gemini APIs.}
\resumeItem{Implemented secure authentication and access control with \textbf{JWT}, \textbf{Google OAuth}, and bcrypt, ensuring compliance-ready data handling.}
\resumeItem{Ensured deployment readiness and maintainability by enhancing system reliability with \textbf{unit/integration testing} and CI/CD pipelines.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Led a 3-person development team to redesign and modernize a client’s small business website, delivering a fully responsive and accessible UI that improved mobile usability and aligned with business goals.}
    \resumeItem{Collaborated directly with the client to iteratively refine features, gathering feedback and implementing design changes that enhanced customer satisfaction and optimized user experience.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} JavaScript, TypeScript, Java, C{\#}, HTML5, CSS3}
  \resumeItem{\textbf{Front-End:} React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
  \resumeItem{\textbf{Back-End \& Cloud:} Node.js, Spring Boot, RESTful APIs, JWT/OAuth, Docker, Git, Linux, GCP }
  \resumeItem{\textbf{Quality \& Practices:} JUnit 5, Jest, CI/CD Pipelines, Agile/Scrum, Code Reviews}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}