\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=cgi\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Engineered a reusable \textbf{JavaScript/jQuery} plugin resulting in reducing bounce rate by \textbf{42\%} on enterprise platforms through streamlined content navigation.}
        \resumeItem{Increased build reliability, reducing \textbf{CI/CD} failures by \textbf{80\%}, by resolving critical \textbf{Node.js} environment mismatches in deployment processes.}
        \resumeItem{Developed an internal microsite, boosting engagement by \textbf{50\%}, using \textbf{PHP} and \textbf{Bootstrap} for modular and dynamic content management.}
        \resumeItem{Enhanced application performance by \textbf{30\%} by integrating \textbf{RESTful} services and optimizing \textbf{React} components for better data flow.}
        \resumeItem{Facilitated global \textbf{Agile} sprints by contributing to backlog refinement, peer reviews, and enhancing \textbf{CI/CD} pipeline efficiency.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com?utm_source=cgi\&utm_medium=resume\&utm_campaign=job_application}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Architected a \textbf{Spring Boot} platform supporting \textbf{500+ users} for real-time practice, using \textbf{React} and \textbf{WebSockets} for live sessions.}
        \resumeItem{Implemented \textbf{Spring Security} for \textbf{JWT}-protected endpoints, ensuring secure role-based access control and session integrity.}
        \resumeItem{Optimized scalability by \textbf{3x} using \textbf{Docker}, \textbf{PostgreSQL}, and refined \textbf{CI/CD} pipelines for efficient deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered an \textbf{AI} interview platform leveraging \textbf{React} and \textbf{Node.js} for dynamic question generation and role-based session management.}
        \resumeItem{Enhanced data handling processes by improving \textbf{JWT} authentication, ensuring secure \textbf{Gemini AI API} interactions.}
        \resumeItem{Streamlined deployment by integrating \textbf{Docker} and comprehensive \textbf{CI/CD} workflows, enabling robust testing and efficient deployment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.bodyblissliz.com}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
      {Project Lead \& Full Stack Web Developer (Capstone)}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Led a 3-member team to deliver a fully responsive website, collaborating with clients to enhance mobile usability and overall user experience.}
        \resumeItem{Partnered with clients to iteratively refine design, incorporating feedback to enhance user satisfaction and streamline interaction processes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}