\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin across portals, accelerating page navigation and reducing bounce rate by \textbf{42\%}.}
        \resumeItem{Resolved complex \textbf{Node.js} versioning conflicts in \textbf{CI/CD} pipelines, reducing build and deployment failures by \textbf{80\%}.}
        \resumeItem{Implemented microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, driving internal user engagement up by \textbf{50\%}.}
        \resumeItem{Elevated \textbf{Lighthouse} SEO and accessibility scores to \textbf{90\%}+ by remediating audit issues across enterprise web assets.}
        \resumeItem{Improved cross-platform UI consistency by enhancing designs in \textbf{Figma} and \textbf{Photoshop}, streamlining enterprise UX workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Developed platform supporting \textbf{500+ users} studying for PLAB 2 using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot}.}
        \resumeItem{Built secure auth with \textbf{JWT}, role-based access, and \textbf{REST APIs} exposing \textbf{60+} backend endpoints.}
        \resumeItem{Integrated \textbf{WebSockets (STOMP)} enabling real-time state sync with consistent latency below \textbf{200ms}.}
        \resumeItem{Optimized backend concurrency with \textbf{PostgreSQL}, \textbf{Docker}, and staged production pipelines.}
        \resumeItem{Deployed full stack via \textbf{Vercel} and \textbf{Render} with custom domain configuration and SSL.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack platform with \textbf{React} and \textbf{Node.js}, incorporating \textbf{Gemini AI APIs} for dynamic question generation.}
        \resumeItem{Implemented secure flows using \textbf{JWT}, \textbf{Google OAuth}, and email-based password resets.}
        \resumeItem{Engineered progress tracking, question pinning, and notes to streamline interview preparation workflows.}
        \resumeItem{Built adaptive UI using \textbf{TailwindCSS}, \textbf{Framer Motion}, and WCAG accessibility standards.}
        \resumeItem{Maintained cloud reliability via \textbf{CI/CD} automation and containerized build workflows.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{}{Live Demo} | \href{https://github.com/altansaid/resume-updates}{GitHub}}
      {AI-Integrated Resume Optimization Workflow}{}
      \resumeItemListStart
        \resumeItem{Built modular \textbf{n8n} workflow triggered via Slack to tailor \LaTeX{} resumes using job description metadata.}
        \resumeItem{Orchestrated \textbf{OpenAI GPT}, HTTP services, and \textbf{GitHub API} to auto-generate and commit resume variants.}
        \resumeItem{Validated \LaTeX{} syntax and sanitized characters before deploying versioned outputs via Git automation.}
        \resumeItem{Created \textbf{JavaScript} transformations for metadata serialization supporting multiple resume output types.}
        \resumeItem{Achieved zero-failure pipeline by integrating fallbacks for invalid \textbf{LLM} output during automated generation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}