\documentclass[letterpaper, 10pt]{article}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[hidelinks]{hyperref}
\usepackage[margin=0.75in]{geometry}
\input{glyphtounicode}
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{
    \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\section}[2]{
    \vspace{10pt}\cvsection{#1}{#2}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubSubItem}[2]{\resumeItem{#1}{\hspace{\fill}#2 \vspace{-2pt}}}
\newcommand{\resumeSubSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.5in, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{{\sc Muhammed Said Altan}} \\
    \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} $|$
    Ottawa, ON, Canada $|$
    \href{https://saidaltan.com}{saidaltan.com} $|$
    \href{https://github.com/altansaid}{github.com/altansaid} $|$
    \href{https://linkedin.com/in/saidaltan}{linkedin.com/in/saidaltan}
\end{center}

\section{Education}{}

\resumeSubHeadingListStart
\resumeSubheading
{Diploma in Web Development and Internet Applications}{2025}
{Algonquin College}{Ottawa, Canada}
\resumeSubHeadingListEnd

\section{Experience}{}

\resumeSubHeadingListStart
\resumeSubheading{Web Developer Intern}{2024-09 -- 2024-12}
{Solace}{Ottawa, Canada}
\resumeItemListStart
\resumeItem{Developed a reusable JavaScript/jQuery table of contents plugin, enhancing navigation and reducing bounce rate by 42\%.}
\resumeItem{Improved SEO and accessibility by addressing audit findings, achieving 90+ scores consistently.}
\resumeItem{Developed an internal employee engagement microsite using PHP and Bootstrap, boosting participation by 50\%.}
\resumeItem{Reduced CI/CD deployment failures by 80\% due to resolving Node.js environment issues.}
\resumeItem{Enhanced full-stack applications by integrating RESTful services, focusing on scalability and secure coding.}
\resumeItem{Collaborated in Agile sprints using Jira, performing code reviews, leading to high maintainability and delivery efficiency.}
\resumeItem{Created improved UI/UX designs, reinforcing internal visual identities with tools like Figma and Adobe Suite.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Leadership}{}

\resumeSubHeadingListStart
\resumeSubheading
{Capstone Project Developer}{2024-01 -- 2024-04}
{BodyBliss}{Ottawa, Canada}
\resumeItemListStart
\resumeItem{Delivered a custom-designed, responsive client website using Laravel and Livewire, meeting all client requirements.}
\resumeItem{Worked closely with clients to gather requirements and deploy a successful final solution.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}{}

\resumeSubHeadingListStart
\resumeSubheading
{PLAB2 Practice Platform}{}{}
{}{}
\resumeItemListStart
\resumeItem{Built a scalable real-time collaborative platform for PLAB 2 exam preparation, incorporating role-based practice sessions.}
\resumeItem{Implemented secure user registration/authentication with JWT, ensuring data security.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Technical Skills}{}

\resumeSubHeadingListStart
\resumeSubSubItem{Programming Languages}{JavaScript, TypeScript, Java, C\#, PHP, SQL, HTML5, CSS3}
\resumeSubSubItem{Frontend Technologies}{React, TypeScript, TailwindCSS, Material UI, Bootstrap, Responsive Design, WCAG}
\resumeSubSubItem{Backend Technologies}{Node.js, REST APIs, JWT/OAuth, Spring Boot, ASP.NET Core, Laravel, Livewire}
\resumeSubSubItem{Databases}{PostgreSQL, MySQL, MongoDB}
\resumeSubSubItem{Tools}{Docker, Git, Linux CLI, Agile/Scrum}
\resumeSubSubItem{Cloud}{Render, Vercel, Google Cloud Platform}
\resumeSubSubItem{Best Practices}{CI/CD, Unit Testing, Code Reviews}
\resumeSubHeadingListEnd

\end{document}