\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}


\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 



\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com?utm_source=electricmind\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(HTML, CSS, React), UI/UX Design, Object-Oriented Programming(JavaScript, C\#) Software Development Lifecycle, Algorithms for Computer Science, Network OS(Linux)} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Engineered reusable JavaScript/jQuery plugins that enhanced navigation speed and reduced bounce rates by \textbf{42\%}, achieving industry-leading user engagement.}
\resumeItem{Resolved Node.js environment mismatch issues, achieving an \textbf{80\% reduction} in CI/CD pipeline failures and enhancing build reliability through precise task management and efficient prototyping.}

\resumeItem{Designed and launched a PHP-based microsite that increased employee engagement by 50\% through secure and modular content distribution leveraging REST APIs and Bootstrap.}

\resumeItem{Optimized interactive front-end components and integrated RESTful services, ensuring scalability and performance with continuous testing and best practice implementation.}

\resumeItem{Executed Agile sprints with cross-functional teams, strengthening maintainability and team collaboration through backlog grooming, peer reviews, and documentation enhancement.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Real-Time Medical Exam Practice Platform}}
{\href{\detokenize{https://plab2practice.com?utm_source=electricmind\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Developed a scalable platform supporting \textbf{500+ active users} with React, TypeScript, and WebSockets, demonstrating cloud-native architecture and real-time collaboration.}
    \resumeItem{Architected secure and modular microservices in Spring Boot with JWT authentication, ensuring reliable and consistent role-based access control.}
    \resumeItem{Enhanced UI accessibility and responsiveness with Material-UI and Tailwind CSS, integrating WCAG-compliant patterns for uniform cross-device experience.}
    \resumeItem{Enabled rapid cloud deployments through Dockerized and PostgreSQL solutions, optimizing for high-concurrency workloads in training workflows.}
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Interview Preparation App}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Built a full-stack interview preparation platform using React and Node.js that generates customized interview questions by integrating advanced AI APIs.}
    
    \resumeItem{Engineered secure user authentication with JWT and Google OAuth, facilitating seamless access control and ensuring enterprise-grade data security.}
    
    \resumeItem{Elevated application deployment readiness with rigorous testing, CI/CD pipeline implementation, and robust containerized configurations.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Spearheaded a development team to redesign a client’s business website, resulting in a fully responsive UI that boosted usability and aligned with strategic business objectives.}
    \resumeItem{Collaborated with clients to iteratively refine features, leveraging direct feedback to maximize user experience and client satisfaction.}
  \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} Java, JavaScript, TypeScript, C{\#}, SQL, HTML5, CSS3}
  \resumeItem{\textbf{Front-End:} React, TailwindCSS, Material-UI, Bootstrap, WebSockets, Responsive \& Accessible Design (WCAG)}
  \resumeItem{\textbf{Back-End \& Cloud:} Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, AWS, Azure }
  \resumeItem{\textbf{Quality \& Practices:} JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Continuous Integration}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}