\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} plugin improving navigation efficiency and reducing bounce rate by \textbf{42\%} across enterprise \textbf{WordPress} knowledge portal.}
        \resumeItem{Resolved environment inconsistencies in \textbf{Node.js}, decreasing build failures in \textbf{CI/CD} pipeline by \textbf{80\%} and enhancing deployment reliability.}
        \resumeItem{Built modular employee microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, boosting user engagement by \textbf{50\%} through decentralized participation.}
        \resumeItem{Corrected SEO and accessibility flaws using \textbf{React}, \textbf{Gatsby}, and \textbf{WCAG} standards, raising Lighthouse scores above \textbf{90+} platform-wide.}
        \resumeItem{Improved cross-platform UI consistency via design assets in \textbf{Figma}, \textbf{Adobe Photoshop}, and \textbf{Illustrator}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Engineered real-time platform serving \textbf{500+ users} with timed case support using \textbf{React}, \textbf{Spring Boot}, and \textbf{WebSockets}.}
        \resumeItem{Built scalable \textbf{JWT}-secured backend with \textbf{60+ REST endpoints} via microservices using \textbf{Spring Boot}.}
        \resumeItem{Attained latency under \textbf{200ms} through optimized STOMP messaging over \textbf{WebSockets} for session role sync.}
        \resumeItem{Containerized \textbf{PostgreSQL} and microservices in \textbf{Docker} to strengthen concurrency management and system reliability.}
        \resumeItem{Deployed full stack across \textbf{Render} and \textbf{Vercel} with CI/CD pipelines under custom domain.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack app using \textbf{React}, \textbf{Node.js}, and \textbf{MongoDB} generating custom questions via \textbf{Gemini AI API}.}
        \resumeItem{Implemented secure authentication with \textbf{Google OAuth}, \textbf{JWT}, and email-based password reset flow.}
        \resumeItem{Added rich UX features--note-taking, pinning, and answer review--via \textbf{React} and \textbf{Framer Motion}.}
        \resumeItem{Secured file upload workflow using \textbf{Multer} with strict input validation to ensure safe handling.}
        \resumeItem{Increased release stability via containerized \textbf{CI/CD pipelines} with test automation and \textbf{TailwindCSS} theming.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{} {Event-Driven AI-Powered Resume Pipeline}{}
      \resumeItemListStart
        \resumeItem{Created automated system in \textbf{n8n} parsing Slack job posts and generating LaTeX resumes using \textbf{OpenAI}.}
        \resumeItem{Retrieved dynamic resume templates and data with \textbf{HTTP Request nodes}, then normalized inputs via \textbf{JavaScript}.}
        \resumeItem{Ensured safe \textbf{GitHub} commits by validating LaTeX structure through custom \textbf{LaTeX parsing} logic.}
        \resumeItem{Maintained error-free delivery through version-controlled outputs and fault-tolerant flow design.}
        \resumeItem{Reduced resume tailoring workload by \textbf{80\%} through end-to-end PDF automation from Slack to deploy.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}