\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=gknot\&utm_medium=resume\&utm_campaign=job_application}{https://saidaltan.com} & [Your Phone Number] \\
  \href{https://linkedin.com/in/saidaltan}{https://linkedin.com/in/saidaltan} & \href{https://github.com/altansaid}{https://github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Algonquin College}{2025-04}
      {Diploma in Web Development and Internet Applications}{Ottawa, Canada}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Solace}{2024-09 -- 2024-12}
      {Web Developer Intern}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Optimized navigation speed by \textbf{42\%} in enterprise systems by creating a reusable \textbf{JavaScript/jQuery} plugin, streamlining Table of Contents access.}
        \resumeItem{Elevated SEO and accessibility ratings to \textbf{90+} by methodically addressing \textbf{Lighthouse} audit recommendations for enterprise platforms.}
        \resumeItem{Boosted internal microsite engagement by \textbf{50\%} using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap} through innovative design solutions and interactive features.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com?utm_source=gknot\&utm_medium=resume\&utm_campaign=job_application}{https://plab2practice.com}}
      {Real-time collaborative platform for medical exam preparation with role-based practice sessions.}{}
      \resumeItemListStart
        \resumeItem{Engineered a real-time platform supporting Doctor, Patient, and Observer roles using \textbf{Spring Boot}, \textbf{React}, and \textbf{WebSockets}, accommodating over \textbf{500+} users.}
        \resumeItem{Advanced feedback tracking across \textbf{28} endpoints using \textbf{secure JWT} and \textbf{WebSockets} for scalable user interactions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app/}{https://interviewcoach-ai.vercel.app/}}
      {MERN stack app generating tailored interview questions with pinning and explanation features.}{}
      \resumeItemListStart
        \resumeItem{Constructed an AI-driven interview platform using \textbf{React} and \textbf{Node.js} to generate questions via \textbf{Gemini AI}, improving preparation by \textbf{30\%}.}
        \resumeItem{Enhanced user experience with \textbf{JWT} authentication and \textbf{Google OAuth} for secure, effortless user sessions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {BodyBliss}{2024-01 -- 2024-04}
      {Capstone Project Developer}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Launched production-ready site with \textbf{custom design} using \textbf{Laravel} and \textbf{Livewire}, aligning precisely with client specifications.}
        \resumeItem{Spearheaded client collaboration for requirement gathering, iterative development, and successful deployment.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} [Java, JavaScript, Python, etc.]}
    \resumeItem{\textbf{Front-End:} [React, TailwindCSS, etc.]}
    \resumeItem{\textbf{Back-End \& Cloud:} [Node.js, Spring Boot, Docker, etc.]}
    \resumeItem{\textbf{Other:} [Git, Agile, Testing, etc.]}
  \resumeItemListEnd

%-------------------------------------------
\end{document}