\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin at enterprise scale, reducing bounce rate by \textbf{42\%} through improved UX and internal navigation.}
        \resumeItem{Improved \textbf{Lighthouse} SEO and accessibility scores to \textbf{90+} by remediating structural HTML issues using \textbf{React} and semantic markup across key pages.}
        \resumeItem{Built responsive microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, boosting cross-functional engagement by \textbf{50\%} through centralized service access.}
        \resumeItem{Resolved \textbf{Node.js} version conflicts in \textbf{CI/CD} environments, reducing deployment failures by \textbf{80\%} and stabilizing release workflows.}
        \resumeItem{Enhanced sprint productivity by collaborating in \textbf{Agile} standups, prioritizing backlog tasks, and participating in peer code reviews to improve delivery cadence.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time tool with \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot}, enabling \textbf{500+} users to collaborate seamlessly with sub-\textbf{200ms} interaction latency.}
        \resumeItem{Designed modular \textbf{JWT}-secured microservices with \textbf{60+ RESTful APIs}, improving scalability and maintainability of critical back-end systems.}
        \resumeItem{Optimized deployment to \textbf{Render} and \textbf{Vercel} using \textbf{Docker}, \textbf{CI/CD} pipelines, and custom domain routing strategies.}
        \resumeItem{Crafted accessible user interface using \textbf{TailwindCSS}, \textbf{Material UI}, and \textbf{WCAG} patterns to ensure inclusive usability across devices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack \textbf{MERN} platform with \textbf{Gemini AI} integration to dynamically generate interview questions based on candidate inputs.}
        \resumeItem{Secured user sessions with \textbf{JWT}, \textbf{Google OAuth}, and \textbf{bcrypt}, supporting multi-role authentication and encrypted access control.}
        \resumeItem{Developed preparation tools including tracking dashboards, rich text note-taking, and pinning features to guide candidate readiness.}
        \resumeItem{Implemented fully responsive UI using \textbf{TailwindCSS} and \textbf{Framer Motion}, meeting inclusive access standards via \textbf{WCAG} compliance.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-updates}{GitHub}}
      {AI-Driven Application Targeting Pipeline}{}
      \resumeItemListStart
        \resumeItem{Automated LaTeX resume updates via \textbf{n8n} flows triggered from Slack, enriching outputs using \textbf{OpenAI} prompts and transformation logic.}
        \resumeItem{Versioned resume changes using \textbf{GitHub REST API} with atomic \textbf{PUT} commits and \textbf{CI/CD} checks for structural validation.}
        \resumeItem{Built LaTeX validation engine in \textbf{JavaScript} to serialize documents, verify layout syntax, and ensure seamless delivery on trigger.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}