\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} plugin for Table of Contents, optimizing UX and reducing bounce rate by \textbf{42\%} across high-traffic internal platforms.}
        \resumeItem{Resolved \textbf{Node.js} versioning conflicts in \textbf{CI/CD} pipeline, decreasing deployment errors by \textbf{80\%} and improving release stability across environments.}
        \resumeItem{Built internal microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee interaction with resources by over \textbf{50\%}.}
        \resumeItem{Elevated SEO and accessibility scores by applying \textbf{Lighthouse} audit recommendations, achieving consistent scores above \textbf{90+} in performance and usability.}
        \resumeItem{Enhanced UI consistency by redesigning components using \textbf{Figma}, \textbf{Photoshop}, and \textbf{Illustrator}, streamlining visuals across internal web tools.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built scalable full-stack platform for \textbf{500+ users} using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot} to enable real-time medical roleplay sessions.}
        \resumeItem{Secured backend with \textbf{JWT authentication} and \textbf{Spring Security}, managing role-based access across \textbf{60+ endpoints} and multiple user types.}
        \resumeItem{Reduced messaging latency to \textbf{<200ms} by optimizing \textbf{WebSocket} architecture and modularizing backend services.}
        \resumeItem{Deployed production-ready system using \textbf{Docker}, \textbf{Render}, and \textbf{Vercel}, supporting seamless access for global user base.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Developed full-stack \textbf{MERN} application integrating \textbf{Gemini AI} to generate personalized prompts and feedback for interview preparation.}
        \resumeItem{Implemented secure user auth with \textbf{JWT}, \textbf{Google OAuth}, and \textbf{bcrypt}, enabling protected sessions and encrypted credential storage.}
        \resumeItem{Enhanced responsive design using \textbf{TailwindCSS} and \textbf{Framer Motion}, improving accessibility and mobile UX.}
        \resumeItem{Enabled rapid deployment with dockerized builds and automated \textbf{CI/CD} pipelines for seamless release cycles.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{}{GitHub} | \href{https://github.com/altansaid/resume-updates}{Repository}}
      {n8n Event-Driven Resume Generation System}{}
      \resumeItemListStart
        \resumeItem{Created Slack-triggered automation pipeline with \textbf{n8n} to generate tailored \textbf{LaTeX resumes} using \textbf{OpenAI GPT} and user input.}
        \resumeItem{Integrated \textbf{GitHub REST API} for version control automation, enabling resume generation and deployment in under \textbf{30 seconds}.}
        \resumeItem{Implemented robust LaTeX validation checks, reducing toolchain formatting errors and deployment issues to near-zero.}
        \resumeItem{Engineered modularized pipeline using \textbf{JavaScript}, \textbf{HTTP}, and \textbf{Base64} logic over nine interconnected automation nodes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}