\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=motorola\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Designed and deployed reusable \textbf{JavaScript/jQuery} Table of Contents plugin on enterprise platforms, enhancing navigation efficiency and reducing bounce rate by \textbf{42\%} through streamlined code optimization.}
        \resumeItem{Resolved complex \textbf{Node.js} environment mismatches, enhancing \textbf{CI/CD} pipeline stability and slashing failures by \textbf{80\%} through targeted configuration updates and scripting improvements.}
        \resumeItem{Developed and supported an internal employee engagement microsite with \textbf{PHP}, \textbf{REST} APIs, and \textbf{Bootstrap}, increasing participation by \textbf{50\%} by integrating interactive user modules.}
        \resumeItem{Boosted SEO performance by resolving \textbf{Lighthouse} issues, achieving scores of \textbf{90+} across metrics by implementing precise corrective coding practices.}
        \resumeItem{Orchestrated \textbf{Agile sprints} with global teams, improving backlog management and peer review quality through proactive communication and process enhancements.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com?utm_source=motorola\&utm_medium=resume\&utm_campaign=job_application}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Engineered a \textbf{Real-time} collaborative platform for \textbf{500+ users} with \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot}, enabling structured sessions with role-based access control and seamless interaction.}
        \resumeItem{Implemented secure \textbf{Spring Boot} microservices with \textbf{JWT} authentication for robust endpoint protection, deploying \textbf{60+ APIs} for adaptive modular functionality.}
        \resumeItem{Optimized scalability with \textbf{PostgreSQL}, \textbf{Docker}, and introduced \textbf{CI/CD} workflows for seamless cloud deployment and continuous integration services.}
        \resumeItem{Created WCAG-compliant, responsive UI with \textbf{TailwindCSS}, ensuring cross-device accessibility and usability consistent with international standards.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Developed comprehensive full-stack platform with \textbf{React} and \textbf{Node.js}, integrating dynamic interview prep questions using \textbf{Gemini AI APIs} for tailored user engagement.}
        \resumeItem{Executed robust \textbf{authentication} and role-based access control via \textbf{JWT} and \textbf{Google OAuth}, ensuring enterprise-compliant data handling processes.}
        \resumeItem{Established thorough \textbf{unit testing}, \textbf{CI/CD} pipelines, and containerized setup, securing advanced deployment and systematic version control.}
        \resumeItem{Crafted modern UI with \textbf{TailwindCSS}, facilitating smooth user experience and bespoke session management for customized preparation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.bodyblissliz.com}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
      {Project Lead \& Full Stack Web Developer (Capstone)}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Led a 3-member team to deliver a fully responsive website, collaborating with clients to enhance mobile usability
and overall user experience.}
        \resumeItem{Partnered with clients to iteratively refine design, incorporating feedback to enhance user satisfaction and streamline interaction processes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}