\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 




\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com?utm_source=goodlifefitness\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(\textbf{HTML}, \textbf{CSS}, \textbf{React}), UI/UX Design, Object-Oriented Programming(\textbf{JavaScript}, \textbf{C\#}) Software Development Lifecycle, Algorithms for Computer Science, Network OS(\textbf{Linux})} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Engineered and deployed reusable \textbf{JavaScript/jQuery} Table of Contents plugin for enterprise knowledge bases, enhancing navigation efficiency and reducing bounce rate by \textbf{42\%} through scalable UI design.}
\resumeItem{Boosted SEO performance and accessibility within complex web environments by remediating \textbf{Lighthouse} audit findings, thereby consistently exceeding \textbf{90+} benchmark scores.}
\resumeItem{Developed an internal employee engagement microsite with \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, driving a \textbf{50\% increase in participation} through secure, modular content reuse.}
\resumeItem{Mitigated \textbf{Node.js} environment mismatch, cutting \textbf{CI/CD} pipeline failures by \textbf{80\%} via targeted script adjustments, enhancing build reliability.}
\resumeItem{Augmented full-stack development by integrating \textbf{RESTful services}, optimizing \textbf{front-end} components for secure, scalable applications.}
\resumeItem{Engaged in \textbf{Agile} sprints with global teams, enhancing my documentation and maintainability practices by participating in peer reviews and implementing \textbf{CI/CD} workflows.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart


\resumeProjectHeading{\textbf{PLAB2 Practice Platform}}
{\href{\detokenize{https://plab2practice.com?utm_source=goodlifefitness\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Developed a real-time collaborative platform for \textbf{500+} users using \textbf{React}, \textbf{TypeScript}, and \textbf{WebSockets (STOMP)}, showcasing cloud-ready architecture.}
    \resumeItem{Engineered secure, role-based \textbf{Spring Boot RESTful microservices} with \textbf{JWT authentication}, delivering 25+ endpoints that align with security standards.}
    \resumeItem{Constructed responsive \textbf{UI} with \textbf{Material-UI} and \textbf{Tailwind CSS}, ensuring WCAG compliance and modern user experience.}
    \resumeItem{Optimized for high concurrency workloads using \textbf{Docker}, \textbf{CI/CD}, and \textbf{PostgreSQL}, enhancing scalability.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Interview Coach AI}}
{\href{https://interviewcoach-ai.vercel.app/}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Constructed an AI-powered interview platform using \textbf{React 19}, \textbf{TailwindCSS}, \textbf{Node.js/Express}, and \textbf{MongoDB}, integrating \textbf{Google's Gemini AI APIs} for scalable design.}
    \resumeItem{Implemented secure, role-based access using \textbf{JWT}, \textbf{Google OAuth}, and \textbf{bcrypt}, ensuring compliance-ready data security.}
    \resumeItem{Elevated deployment reliability through \textbf{unit/integration testing}, \textbf{CI/CD} pipelines, and containerized configurations.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Directed a 3-person team to redesign and modernize a client’s business website, delivering a responsive UI improving mobile usability and aligning with business goals.}
    \resumeItem{Collaborated directly with client for iterative feature refinement, implementing design changes that enhanced satisfaction and user experience.}
  \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} \textbf{Java}, \textbf{JavaScript}, \textbf{TypeScript}, \textbf{C{\#}}, \textbf{SQL}, \textbf{HTML5}, \textbf{CSS3}}
  \resumeItem{\textbf{Front-End:} \textbf{React}, \textbf{Redux}, \textbf{TailwindCSS}, \textbf{Material UI}, \textbf{WebSockets}, Responsive \& Accessible Design (\textbf{WCAG})}
  \resumeItem{\textbf{Back-End \& Cloud:} \textbf{Spring Boot}, \textbf{Node.js}, \textbf{RESTful APIs}, \textbf{JWT/OAuth}, \textbf{Docker}, \textbf{Git}, \textbf{Linux}, \textbf{Azure} \& \textbf{GCP} }
  \resumeItem{\textbf{Quality \& Practices:} \textbf{JUnit 5}, \textbf{Jest}, \textbf{React Testing Library}, \textbf{CI/CD Pipelines}, \textbf{Agile/Scrum}, \textbf{Code Reviews}}
\resumeItemListEnd




\resumeSubHeadingListEnd
\end{document}