\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 

\begin{document}

\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com/?utm_source=avanade\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(HTML, CSS, React), UI/UX Design, Object-Oriented Programming(JavaScript, C\#) Software Development Lifecycle, Algorithms for Computer Science, Network OS(Linux)} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Engineered a scalable \textbf{JavaScript/jQuery} Table of Contents plugin for web platforms, improving navigation efficiency and reducing bounce rate by \textbf{42\%} via advanced UI techniques.}
\resumeItem{Diagnosed and resolved \textbf{Node.js} environment inconsistencies, cutting CI/CD pipeline failures by \textbf{80\%} through enhanced build environment standardization.}
\resumeItem{Developed an internal microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, driving a \textbf{50\%} increase in employee engagement through secure, modular content delivery.}
\resumeItem{Integrated \textbf{RESTful services} for full-stack development to boost application scalability and security with best practices.}
\resumeItem{Collaborated on \textbf{Agile sprints} with international teams, elevating maintainability and delivery through comprehensive documentation and systematic reviews.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{PLAB2 Practice Platform}}
{\href{\detokenize{https://plab2practice.com/?utm_source=avanade\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Established a real-time, multi-user collaboration platform using \textbf{React}, \textbf{TypeScript}, and \textbf{WebSockets (STOMP)}, supporting \textbf{500+ users} for synchronized, secure practice sessions on a scalable infrastructure.}
    
    \resumeItem{Deployed modular \textbf{Spring Boot RESTful microservices} with \textbf{JWT authentication}, meeting stringent government security standards through robust integration.}
    
    \resumeItem{Developed a modern \textbf{UI system} with \textbf{Material-UI} and \textbf{Tailwind CSS}, ensuring responsive design compliance with WCAG standards across all devices.}
    
    \resumeItem{Enhanced performance for \textbf{high-concurrency workloads} with \textbf{PostgreSQL} and \textbf{Dockerized deployments}, ensuring reliability in cloud environments.}
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Interview Preparation App}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Launched a cloud-native platform with \textbf{React 19}, \textbf{TailwindCSS}, \textbf{Node.js}, and \textbf{MongoDB}, creating \textbf{AI-driven} interview questions leveraging \textbf{Gemini AI APIs}.}
    
    \resumeItem{Implemented robust \textbf{authentication} and \textbf{role-based access control} using \textbf{JWT} and \textbf{Google OAuth} to strengthen security measures.}
    
    \resumeItem{Boosted deployment readiness via \textbf{unit/integration testing}, \textbf{CI/CD} pipelines, and containerized configurations for sustainable operations.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Led a 3-person team to redesign a business site, delivering a responsive UI that enhanced mobile usability and met strategic goals.}
    \resumeItem{Collaboratively refined features with client feedback, optimizing user experience and aligning with customer satisfaction goals.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} Java, JavaScript, TypeScript, C{\#}, SQL, HTML5, CSS3}
  \resumeItem{\textbf{Front-End:} React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
  \resumeItem{\textbf{Back-End \& Cloud:} Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP }
  \resumeItem{\textbf{Quality \& Practices:} JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}