\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 




\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com/?utm_source=jonas\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(\textbf{HTML}, \textbf{CSS}, \textbf{React}), UI/UX Design, Object-Oriented Programming(\textbf{JavaScript}, \textbf{C\#}) Software Development Lifecycle, Algorithms for Computer Science, Network OS(\textbf{Linux})} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Developed and deployed reusable \textbf{JavaScript/jQuery} navigation plugin, enhancing speed by \textbf{42\%} within enterprise apps through scalable \textbf{UI} and accessibility standards.}
\resumeItem{Resolved \textbf{Node.js} environment mismatch, decreasing \textbf{CI/CD} failures by \textbf{80\%} in production pipelines through refined configuration management.}
\resumeItem{Built internal microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, raising participation by \textbf{50\%} via secure, modular content reuse across teams.}
\resumeItem{Integrated \textbf{RESTful services} to optimize \textbf{front-end} and enforce performance/security best practices in scalable applications.}
\resumeItem{Collaborated on \textbf{Agile sprints} with distributed teams, enhancing maintainability through backlog refinement, peer review, and \textbf{CI/CD} integration.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{PLAB2 Practice Platform}}
{\href{\detokenize{https://plab2practice.com/?utm_source=jonas\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Developed \textbf{500+} user real-time platform using \textbf{React}, \textbf{TypeScript}, and \textbf{WebSockets}, demonstrating scalable, cloud-ready design for synchronized practice sessions.}
    
    \resumeItem{Engineered \textbf{Spring Boot RESTful microservices} with \textbf{JWT}, enabling secure, 25+ endpoint architecture meeting government security standards.}
    
    \resumeItem{Created modern \textbf{UI} with \textbf{Material-UI} and \textbf{Tailwind CSS}, ensuring \textbf{WCAG-compliance} for performance across devices.}
    
    \resumeItem{Optimized concurrency using \textbf{PostgreSQL} and \textbf{Docker}, supporting digital modernization in high-demand environments.}
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{Interview Coach AI}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Launched \textbf{full-stack} platform with \textbf{React 19}, \textbf{TailwindCSS}, \textbf{Node.js/Express}, integrating \textbf{Gemini AI APIs} for scalable interview simulations.}
    
    \resumeItem{Integrated secure authentication and control (\textbf{JWT}, \textbf{Google OAuth}, \textbf{bcrypt}), complying with enterprise data handling standards.}
    
    \resumeItem{Boosted deployment readiness by implementing \textbf{unit/integration testing} and \textbf{CI/CD pipelines} for seamless cloud distribution.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Guided 3-person team to overhaul client website, delivering fully responsive \textbf{UI} that enhanced mobile usability, aligning with business goals.}
    \resumeItem{Partnered with client to iteratively refine features, boosting satisfaction by optimizing user experience through actionable design changes.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} \textbf{Java}, \textbf{JavaScript}, \textbf{TypeScript}, \textbf{C\#}, \textbf{SQL}, \textbf{HTML5}, \textbf{CSS3}}
  \resumeItem{\textbf{Front-End:} \textbf{React}, \textbf{Redux}, \textbf{TailwindCSS}, \textbf{Material UI}, \textbf{WebSockets}, Responsive \& Accessible Design (\textbf{WCAG})}
  \resumeItem{\textbf{Back-End \& Cloud:} \textbf{Spring Boot}, \textbf{Node.js}, \textbf{RESTful APIs}, \textbf{JWT/OAuth}, \textbf{Docker}, \textbf{Git}, \textbf{Linux}, \textbf{Azure} \& \textbf{GCP} }
  \resumeItem{\textbf{Quality \& Practices:} \textbf{JUnit 5}, \textbf{Jest}, \textbf{React Testing Library}, \textbf{CI/CD} Pipelines, \textbf{Agile/Scrum}, Code Reviews}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}