\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin across internal platforms, reducing navigation time by \textbf{42\%} and enhancing UI consistency enterprise-wide.}
        \resumeItem{Resolved \textbf{Node.js} \textbf{CI/CD} build issues in multi-env pipelines, cutting deployment errors by \textbf{80\%} and ensuring stable releases across dev and staging.}
        \resumeItem{Built cross-department microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee engagement by \textbf{50\%} within 8 weeks of launch.}
        \resumeItem{Optimized accessibility and SEO through \textbf{Lighthouse} audits, raising core scores to \textbf{90+} and ensuring compliance with modern web standards.}
        \resumeItem{Enhanced UI consistency using \textbf{Figma} and \textbf{Adobe} assets, improving brand alignment across employee-facing internal web tools.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built scalable full-stack platform for \textbf{500+ users} using \textbf{Spring Boot}, \textbf{React}, and \textbf{WebSockets}, achieving sub-\textbf{200ms} response latency.}
        \resumeItem{Designed \textbf{RESTful APIs} with \textbf{Spring Security}, implementing \textbf{60+} endpoints to support secure role-based sessions and feedback features.}
        \resumeItem{Implemented \textbf{JWT}-based auth with custom roles for \textbf{Doctors}, \textbf{Patients}, and \textbf{Observers} within live collaborative sessions.}
        \resumeItem{Deployed production-ready system using \textbf{Docker}, \textbf{PostgreSQL}, and automated \textbf{CI/CD} pipelines on \textbf{Render} and \textbf{Vercel}.}
        \resumeItem{Developed fully responsive UI with \textbf{React}, \textbf{TypeScript}, and \textbf{TailwindCSS}, aligned with WCAG accessibility standards.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack app using \textbf{React} and \textbf{Node.js}, integrating \textbf{Gemini AI} to generate personalized interview questions in real time.}
        \resumeItem{Secured application with \textbf{JWT}, \textbf{Google OAuth}, and email-based reset flow using \textbf{bcrypt} for encrypted user auth.}
        \resumeItem{Added dynamic note-taking and pinning system to boost candidate recall and personalized session workflows.}
        \resumeItem{Enhanced mobile usability via \textbf{TailwindCSS} and \textbf{Framer Motion}, ensuring full WCAG-compliant accessibility across devices.}
        \resumeItem{Implemented test coverage, containerization, and \textbf{CI/CD} to support reliable, scalable production deployments.}
      \resumeItemListEnd

    \resumeSubheading
  {\textbf{Restaurant Review Management System}}{\href{https://github.com/altansaid/restaurantreviewmanagementsystem}{GitHub}}{Full-Stack Review Platform}{}
  \resumeItemListStart
   \resumeItem{Built modular backend in \textbf{C\#} with \textbf{ASP.NET Core} MVC, introducing layered error handling and form validation for stable runtime outcomes.}
   \resumeItem{Created dynamic frontend using \textbf{React}, Hooks, and \textbf{Bootstrap 5} to manage live form inputs with client-side validation.}
   \resumeItem{Added moderation dashboard enabling admin review sorting, improving flagged feedback resolution time by \textbf{35\%}.}
   \resumeItem{Persisted filtered reviews via \textbf{SQL} database using RESTful patterns, enhancing query speed and clarity.}
   \resumeItem{Completed unit-tested full-stack features aligned with academic specs using MVC routing and controller logic.}
  \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}