\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 

\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com/?utm_source=electricmindfullstack\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(HTML, CSS, React), UI/UX Design, Object-Oriented Programming(JavaScript, C\#) Software Development Lifecycle, Algorithms for Computer Science, Network OS(Linux)} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://solace.com/}{Solace}}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Engineered reusable \textbf{JavaScript/jQuery} Table of Contents plugin for large-scale knowledge bases, cutting bounce rates by \textbf{42\%} via accessibility-focused design and efficient UI navigation.}
\resumeItem{Rectified \textbf{Node.js} environment mismatches, slashing \textbf{CI/CD} pipeline failures by \textbf{80\%} through version standardization and dependency updates.}
\resumeItem{Constructed employee engagement microsite using \textbf{PHP, REST APIs, and Bootstrap}, boosting engagement by \textbf{50\%} through secure, modular content frameworks.}
\resumeItem{Enhanced \textbf{front-end} by incorporating \textbf{RESTful services}, reinforcing security, and ensuring performance best practices for highly scalable solutions.}
\resumeItem{Facilitated \textbf{Agile} methodologies in global teams, improving project delivery by contributing to sprints, enhancing documentation, and optimizing cross-functional workflows.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Real-Time Medical Exam Practice Platform}}
{\href{\detokenize{https://plab2practice.com/?utm_source=electricmindfullstack\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Developed multi-user collaboration platform using \textbf{React, TypeScript, and WebSockets (STOMP)}, supporting \textbf{500+} users with real-time role-based sessions, showcasing scalable cloud-ready capabilities.}
    \resumeItem{Architected secure \textbf{Spring Boot RESTful microservices} with \textbf{JWT authentication}, aligning \textbf{25+} APIs with robust government standards for improved service maintenance.}
    \resumeItem{Implemented modern UI system using \textbf{Material-UI} and \textbf{Tailwind CSS}, deploying \textbf{WCAG}-compliant design patterns for consistent accessibility across all devices.}
    \resumeItem{Improved system performance via \textbf{PostgreSQL}, \textbf{Dockerized} deployments, and \textbf{CI/CD}, ensuring reliability under high concurrency workloads.}
\resumeItemListEnd

\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Interview Preparation App}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Launched \textbf{cloud-native full-stack} platform with \textbf{React 19, TailwindCSS}, and \textbf{Node.js/Express, MongoDB}, integrating \textbf{Google’s Gemini AI APIs} for dynamic interview preparation resources.}
    \resumeItem{Executed secure \textbf{authentication} and \textbf{access control} (\textbf{JWT, Google OAuth, bcrypt}), refining user workflows for compliance-ready data practices.}
    \resumeItem{Increased system readiness by integrating \textbf{unit/integration testing}, \textbf{CI/CD} pipelines, and containerized app structures for scalable service deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Directed 3-person team to overhaul client business website, achieving substantial mobile usability improvements via fully responsive, accessible UI that aligned with strategic objectives.}
    \resumeItem{Partnered with client in iterative refinements by gathering feedback and integrating design changes, which increased customer satisfaction and optimized user engagement.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} Java, JavaScript, TypeScript, C{\#}, SQL, HTML5, CSS3}
  \resumeItem{\textbf{Front-End:} React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
  \resumeItem{\textbf{Back-End \& Cloud:} Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP }
  \resumeItem{\textbf{Quality \& Practices:} JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
\resumeItemListEnd

\resumeSubHeadingListEnd
\end{document}