\documentclass[letterpaper, 10pt]{article}

% Packages
\usepackage{latexsym, enumitem}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{array}
\usepackage{url}
\usepackage{fancyhdr}

% Macros
\newcommand{\resumeItem}[1]{\item #1 }
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubSubItem}[2]{\resumeItem{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeProjectHeading}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \url{#2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeTechSkill}[2]{\resumeSubItem{#1}{#2}}
\newcommand{\resumeEducation}[3]{\item #1, #2, #3 \vspace{-2pt}}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{0.75in}
\addtolength{\topmargin}{-0.375in}
\addtolength{\textheight}{0.75in}

% Sections formatting
\titlespacing{\section}{0pt}{5pt}{5pt}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]

% Custom header/footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{Muhammed Said Altan}
\fancyfoot[C]{\thepage}

\begin{document}

% Header
\begin{center}
    \textbf{\Huge Muhammed Said Altan} \\ \vspace{2pt}
    Ottawa, ON, Canada \\ \vspace{2pt}
    \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} $|$ 
    \url{https://saidaltan.com} $|$
    \url{https://linkedin.com/in/saidaltan} $|$
    \url{https://github.com/altansaid}
\end{center}

% Education
\section{Education}
\resumeEducation{Diploma in Web Development and Internet Applications}{Algonquin College}{Graduation: April 2025}

% Experience
\section{Experience}
\resumeSubheading{Web Developer Intern}{Solace}{Ottawa, Canada}{Sept 2024 -- Dec 2024}
\resumeItemListStart
\resumeItem{Developed a scalable JavaScript/jQuery Table of Contents plugin, streamlining enterprise knowledge base navigation, boosting user engagement by 42\%.}
\resumeItem{Enhanced frontend performance and accessibility in React applications by addressing key SEO and Lighthouse audit issues, consistently achieving 90+ scores.}
\resumeItem{Built a responsive, accessible internal microsite using React and Bootstrap, elevating departmental content reuse and increasing engagement by 50\%.}
\resumeItem{Optimized CI/CD pipelines by resolving Node.js discrepancies, slashing build failures by 80\% and enhancing deployment reliability.}
\resumeItem{Integrated RESTful services efficiently with React, ensuring scalable and secure full-stack solutions in Agile sprints.}
\resumeItem{Collaborated in Agile teams, executing peer code reviews and CI/CD workflows to reinforce best practices.}
\resumeItem{Improved UI/UX designs in Figma, Adobe Photoshop, and Illustrator, aligning with accessible design standards.}
\resumeItemListEnd

% Leadership
\section{Leadership}
\resumeSubheading{Capstone Project Developer}{BodyBliss}{Ottawa, Canada}{Jan 2024 -- Apr 2024}
\resumeItemListStart
\resumeItem{Delivered a customized, responsive website using Laravel and Livewire, facilitating client requirements through iterative development.}
\resumeItem{Managed the entire project lifecycle, ensuring on-time delivery of the final product.}
\resumeItemListEnd

% Projects
\section{Projects}
\resumeProjectHeading{PLAB2 Practice Platform}{https://plab2practice.com}
\resumeItemListStart
\resumeItem{Built a real-time collaborative platform for exam preparation with role-based session features, enhancing user engagement.}
\resumeItem{Implemented secure authentication and role-based access using JWT and Spring Security to protect user data.}
\resumeItemListEnd

\resumeProjectHeading{Interview Coach AI}{https://interviewcoach-ai.vercel.app/}
\resumeItemListStart
\resumeItem{Developed a cloud-native full-stack app with React and Node.js, providing AI-powered interview questions and preparation tools.}
\resumeItem{Enhanced frontend responsiveness and scalability in mobile-friendly interfaces, integrating Google’s Gemini AI for personalized questions.}
\resumeItemListEnd

% Technical Skills
\section{Technical Skills}
\resumeTechSkill{Languages}{JavaScript, TypeScript, Java, PHP, SQL, HTML5, CSS3}
\resumeTechSkill{Frontend}{React, TailwindCSS, Material UI, Bootstrap, Responsive Design, WCAG}
\resumeTechSkill{Backend}{Node.js, REST APIs, JWT/OAuth}
\resumeTechSkill{Databases}{PostgreSQL, MongoDB}
\resumeTechSkill{Tools}{Git, Docker, Linux CLI}
\resumeTechSkill{Cloud Platforms}{Vercel, Supabase}
\resumeTechSkill{Practices}{Agile/Scrum, CI/CD, Unit Testing}
\end{document}