\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Reduced bounce rate by \textbf{42\%} across enterprise sites by developing reusable \textbf{JavaScript/jQuery} Table of Contents plugin improving in-page navigation and engagement.}
        \resumeItem{Resolved \textbf{Node.js} build chain version conflicts, reducing \textbf{CI/CD} deployment failures by \textbf{80\%} and accelerating production delivery cycles.}
        \resumeItem{Improved accessibility and SEO Lighthouse scores to \textbf{90+} by fixing structural \textbf{HTML} issues and streamlining content workflows.}
        \resumeItem{Boosted internal engagement by \textbf{50\%} through launch of microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs} for dynamic interaction.}
        \resumeItem{Enhanced interface consistency across internal tools using \textbf{Figma}, \textbf{Adobe Photoshop}, and \textbf{Illustrator} to iterate UI/UX designs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Built personalized question engine using \textbf{React}, \textbf{Node.js}, and \textbf{Gemini AI}, generating \textbf{dynamic content} customized to user-provided input.}
        \resumeItem{Integrated secure \textbf{JWT} and \textbf{Google OAuth} auth system with email-password reset for streamlined user onboarding experience.}
        \resumeItem{Improved cross-device accessibility using \textbf{TailwindCSS} and \textbf{Framer Motion}, delivering WCAG-compliant responsive UI.}
        \resumeItem{Maintained code base reliability using modular \textbf{REST APIs}, \textbf{CI/CD} pipelines, and Dockerized architecture.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Supported \textbf{500+ users} in doctor-patient simulations using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot} stack.}
        \resumeItem{Achieved real-time session sync under \textbf{200ms latency} using \textbf{WebSocket STOMP} protocol managing multi-role interaction.}
        \resumeItem{Created WCAG-compliant UI using \textbf{TailwindCSS}, \textbf{Material UI}, and dynamic \textbf{TypeScript} components.}
        \resumeItem{Scaled services by deploying microservices with \textbf{Docker} and \textbf{PostgreSQL} via \textbf{Render} and \textbf{Vercel}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{}{GitHub} | \href{https://github.com/altansaid/resume-updates}{GitHub}}
      {AI-Integrated Resume Optimization Workflow}{}
      \resumeItemListStart
        \resumeItem{Automated LaTeX resume generation using \textbf{n8n}, \textbf{Slack}, and \textbf{OpenAI GPT}, triggered dynamically from job descriptions.}
        \resumeItem{Generated tailored bullet points merging resume structure with contextual inference for consistent \textbf{X-Y-Z} achievement formatting.}
        \resumeItem{Versioned compiled resume PDFs through GitHub commits via \textbf{REST APIs}, Base64 encoding, and structured JSON.}
        \resumeItem{Validated documents for \textbf{LaTeX} syntax pre-deployment, ensuring error-free formats in all saved versions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}