\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=euna\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com?utm_source=euna\&utm_medium=resume\&utm_campaign=job_application} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Engineered and launched a reusable \textbf{JavaScript/jQuery} Table of Contents plugin for enterprise platforms, enhancing navigation efficiency and reducing bounce rate by \textbf{42\%} through modular design.}
        \resumeItem{Diagnosed and corrected \textbf{Node.js} environment mismatches, reducing \textbf{CI/CD} pipeline failures by \textbf{80\%} by implementing \textbf{automated testing} and detailed configuration management.}
        \resumeItem{Built and maintained an internal employee engagement microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing participation by \textbf{50\%} through intuitive interface design and user-centric features.}
        \resumeItem{Enhanced full-stack development by integrating \textbf{RESTful services}, optimizing \textbf{React} components, and reinforcing security through rigorous \textbf{OWASP} compliance in a high-traffic system.}
        \resumeItem{Facilitated \textbf{Agile sprints} with global teams by leading backlog refinement sessions, performing peer reviews, and streamlining \textbf{CI/CD} processes for continuous delivery.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com?utm_source=euna\&utm_medium=resume\&utm_campaign=job_application}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built a real-time collaborative platform for PLAB 2 exam preparation, enabling \textbf{500+} users using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot} through scalable architecture design.}
        \resumeItem{Implemented secure \textbf{microservices} with \textbf{JWT authentication} for maintainability and scalability across \textbf{25+} endpoints by employing microservices architecture patterns.}
        \resumeItem{Optimized system using \textbf{PostgreSQL} and \textbf{Docker}, enabling high concurrency and improving responsiveness by \textbf{60\%} through efficient indexing and container orchestration.}
        \resumeItem{Delivered \textbf{CI/CD}-ready configuration, facilitating smooth deployments on \textbf{Render} and \textbf{Vercel}, achieving \textbf{95\%} deployment success rate.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered a comprehensive full-stack platform using \textbf{React} and \textbf{Node.js}, integrating \textbf{Gemini AI APIs} to tailor interview prep questions dynamically, enhancing user preparation strategies.}
        \resumeItem{Implemented robust \textbf{authentication}, role-based access control, and enterprise-compliant data handling, increasing security compliance by \textbf{30\%} through strict policy frameworks.}
        \resumeItem{Prepared for deployment with thorough \textbf{unit testing}, \textbf{CI/CD pipelines}, and containerized setup, increasing reliability and reducing errors by \textbf{40\%}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.bodyblissliz.com}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
      {Project Lead \& Full Stack Web Developer (Capstone)}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Led a 3-member team to deliver a fully responsive website, collaborating with clients to enhance mobile usability and overall user experience.}
        \resumeItem{Partnered with clients to iteratively refine design, incorporating feedback to enhance user satisfaction and streamline interaction processes.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}