\documentclass[letterpaper, 10pt]{article}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{array}
\usepackage{verbatim}
\usepackage{multicol}
\usepackage{blindtext}
\usepackage{titlesec}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\titlerule\vspace{-8pt}]
\titlespacing{\section}{0pt}{0pt}{0pt}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{0.75in}
\addtolength{\topmargin}{-0.375in}
\addtolength{\textheight}{0.75in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}{: #2 \vspace{-4pt}}}}

\newcommand{\resumeSubheadingSubSubheading}[1]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\textit{\small#1}} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\itemsepAdjust}{\setlength{\itemsep}{5pt}}
\newcommand{\itemsepAdjustDouble}{\setlength{\itemsep}{10pt}}

\newcommand{\section}[1]{
  \vspace{4pt}\textsc{\large} \textbf{#1}
  \vspace{2pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeSubItemsStart}{\begin{itemize}[label=--]}
\newcommand{\resumeSubItemsEnd}{\end{itemize}}

\begin{document}

\begin{center}
    \textbf{\Huge {\scshape Muhammed Said Altan}} \\ \vspace{1pt}
    Ottawa, ON, Canada \\ \vspace{1pt}
    \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} $ | $
    \href{https://saidaltan.com}{saidaltan.com} $ | $
    \href{https://github.com/altansaid}{github.com/altansaid} $ | $
    \href{https://linkedin.com/in/saidaltan}{linkedin.com/in/saidaltan}
\end{center}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Diploma in Web Development and Internet Applications}{Apr 2025}
      {Algonquin College}{Ottawa, Canada}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{Sep 2024 -- Dec 2024}
      {Solace}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Enhanced frontend scalability and performance by integrating React components with existing JavaScript infrastructure, improving client-side load efficiency.}
        \resumeItem{Addressed and resolved key SEO and accessibility issues identified in audits using focused optimizations, consistently achieving scores above 90+.}
        \resumeItem{Utilized REST APIs and React to build a responsive internal microsite, significantly increasing employee engagement through improved UI/UX design.}
        \resumeItem{Streamlined the CI/CD pipeline by solving Node.js compatibility issues, reducing build failures by 80\%.}
        \resumeItem{Collaborated with Agile teams to iterate on frontend features, ensuring responsive and accessible UIs for diverse platforms.}
        \resumeItem{Crafted impactful UI/UX designs using Figma, Adobe Photoshop, and Illustrator, enhancing visual aesthetics of internal digital products.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PLAB2 Practice Platform}{}
      {Collaborative Exam Prep Tool}{}
      \resumeItemListStart
        \resumeItem{Developed a scalable web application for PLAB2 exam prep, engaging users in real-time sessions with comprehensive feedback loops.}
        \resumeItem{Implemented a modular architecture using React, TypeScript, and Spring Boot, supporting robust and secure user authentication.}
      \resumeItemListEnd
    \resumeSubheading
      {Interview Coach AI}{}
      {AI-Powered Interview Tool}{}
      \resumeItemListStart
        \resumeItem{Engineered a MERN stack platform generating personalized interview questions, enhancing candidate readiness in a responsive UI.}
        \resumeItem{Incorporated JWT and OAuth for secure, streamlined authentication, ensuring compliance with modern security practices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}{JavaScript, TypeScript, Java, C\#, PHP, HTML5, CSS3}
    \resumeSubItem{Frontend}{React, TailwindCSS, Material-UI, Bootstrap, Responsive Design, WCAG Compliance}
    \resumeSubItem{Backend}{Node.js, Spring Boot, REST APIs, JWT/OAuth}
    \resumeSubItem{Databases}{PostgreSQL, MongoDB, MySQL}
    \resumeSubItem{Tools}{Docker, Git, Linux CLI}
    \resumeSubItem{Cloud Platforms}{Render, Vercel, Google Cloud Platform}
    \resumeSubItem{Practices}{Agile/Scrum, CI/CD, Unit Testing, Clean Architecture, Code Reviews}
  \resumeSubHeadingListEnd

\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Capstone Project Developer}{Jan 2024 -- Apr 2024}
      {BodyBliss}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Delivered a production-ready client website with Laravel, achieving custom, responsive design and UI.}
        \resumeItem{Collaborated with clients to iteratively refine features and deploy solutions aligning with their business needs.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}