\documentclass[letterpaper, 10pt]{article}

% Packages and settings
\usepackage{latexsym}
\usepackage{enumitem}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{hyperref}
\usepackage{fancyhdr}

% Set header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[C]{\bfseries Muhammed Said Altan's Resume}
\fancyfoot[C]{\thepage}

% Section settings
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{\textbf{#1}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-0.5em}\item 
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-1em}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-0.2em}}
\newcommand{\resumeSubHeadingListStart}{
  \begin{itemize}[leftmargin=0.5cm, label={}]
}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{
  \begin{itemize}[leftmargin=0.5cm, label={\textbullet}, itemsep = 0.5em]
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-0.5em}}

% Document content
\begin{document}

% Personal Information
\begin{center}
    \textbf{\Huge Muhammed Said Altan} \\ 
    Ottawa, ON, Canada | \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} | 
    \href{https://saidaltan.com}{saidaltan.com} | \href{https://github.com/altansaid}{GitHub} | 
    \href{https://linkedin.com/in/saidaltan}{LinkedIn}
\end{center}

% Education
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
      {Algonquin College}{Ottawa, Canada}
      {Diploma in Web Development and Internet Applications; GPA: 4.0}{Expected Apr 2025}
\resumeSubHeadingListEnd

% Experience
\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{Sep 2024 - Dec 2024}
      {Solace}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Engineered a reusable JavaScript/jQuery Table of Contents plugin for enterprise knowledge bases, improving navigation speed and reducing bounce rate by 42%.}
        \resumeItem{Improved SEO performance and accessibility by addressing Lighthouse audit findings, raising performance and accessibility scores consistently above 90+.}
        \resumeItem{Developed an internal employee engagement microsite using PHP and Bootstrap, increasing participation by 50% and enabling modular content reuse.}
        \resumeItem{Resolved Node.js CI/CD pipeline issues, reducing deployment failures by 80% and enhancing reliability across environments.}
        \resumeItem{Integrated RESTful services with frontend components, focusing on scalable and secure coding practices.}
        \resumeItem{Collaborated in Agile sprints with global teams, contributing to backlog grooming, peer code reviews, and strengthening CI/CD workflows.}
        \resumeItem{Designed and enhanced UI/UX elements using Figma and Adobe tools, elevating user experience and visual identity.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

% Projects
\section{Projects}
\resumeSubHeadingListStart
    \resumeSubheading
      {PLAB2 Practice Platform}{\href{https://plab2practice.com}{plab2practice.com}}
      {GitHub Repo}{}
      \resumeItemListStart
        \resumeItem{Created a collaborative platform for PLAB 2 exam preparation with role-based sessions, enhancing real-time practice capabilities for medical professionals.}
        \resumeItem{Developed secure user authentication and role-based access control, ensuring controlled session participation and feedback workflows.}
        \resumeItem{Implemented real-time synchronization with WebSockets and ensured application scalability with PostgreSQL and Dockerized services.}
      \resumeItemListEnd

    \resumeSubheading
      {Interview Coach AI}{\href{https://interviewcoach-ai.vercel.app/}{interviewcoach-ai.vercel.app}}
      {GitHub Repo}{}
      \resumeItemListStart
        \resumeItem{Built a MERN stack platform for AI-generated interview questions, providing personalized interview preparation with note-taking features.}
        \resumeItem{Integrated Google’s Gemini AI API for generating targeted technical and behavioral interview questions.}
        \resumeItem{Enhanced user experience with a responsive UI using TailwindCSS and smooth animations via Framer Motion.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

% Technical Skills
\section{Technical Skills}
\resumeSubHeadingListStart
    \resumeSubItem{Programming Languages}{: JavaScript, TypeScript, Java, PHP, C\#, SQL}
    \resumeSubItem{Frontend Development}{: React, Redux, TailwindCSS, Material UI, Bootstrap}
    \resumeSubItem{Backend Development}{: Node.js, Spring Boot, ASP.NET Core, Laravel}
    \resumeSubItem{Databases}{: PostgreSQL, MySQL, MongoDB}
    \resumeSubItem{Tools \& Platforms}{: Docker, Git, Linux CLI, Render, Vercel}
    \resumeSubItem{Practices}{: Agile/Scrum, CI/CD, Unit Testing (Jest, JUnit), Code Reviews}
\resumeSubHeadingListEnd

% Leadership
\section{Leadership}
\resumeSubHeadingListStart
    \resumeSubheading
      {Capstone Project Developer}{Jan 2024 - Apr 2024}
      {BodyBliss}{Ottawa, Canada}
      \resumeItemListStart
        \resumeItem{Delivered a production-ready client website with custom design and responsive UI using Laravel and Livewire.}
        \resumeItem{Collaborated with client to gather requirements, iterate on features, and deploy final solution proficiently.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}