\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin for documentation sites, decreasing bounce rate by \textbf{42\%} through enhanced navigation experience.}
        \resumeItem{Resolved \textbf{Node.js} version conflicts across environments, increasing production deployment reliability by \textbf{80\%} on existing \textbf{CI/CD} pipeline.}
        \resumeItem{Launched internal microsite with \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing engagement by \textbf{50\%} through modular, user-friendly architecture.}
        \resumeItem{Raised Lighthouse SEO and accessibility scores to \textbf{90+} by applying semantic markup and optimizing with \textbf{React} and \textbf{Gatsby}.}
        \resumeItem{Unified UI across teams by applying shared \textbf{Figma} styles and \textbf{Adobe} assets during global \textbf{Agile} sprints.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built simulation platform for \textbf{500+ users} using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot} enabling synchronized real-time PLAB2 exam practice.}
        \resumeItem{Designed \textbf{microservices} with \textbf{JWT} and over \textbf{60+} \textbf{RESTful APIs} to support modular, role-based medical scenarios.}
        \resumeItem{Reduced latency to under \textbf{200ms} by tuning session lifecycles and integrating \textbf{PostgreSQL} with containerized \textbf{Docker} networking.}
        \resumeItem{Improved UI accessibility and responsiveness using modular \textbf{TypeScript} components and \textbf{TailwindCSS}.}
        \resumeItem{Deployed seamlessly to \textbf{Render} and \textbf{Vercel} with automated \textbf{CI/CD} flows and custom domain provisioning.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Created role-adaptive interview coach using \textbf{React}, \textbf{Node.js}, and \textbf{Gemini AI API} to generate targeted question sets.}
        \resumeItem{Enhanced user data security with \textbf{JWT}, \textbf{Google OAuth}, and \textbf{bcrypt}, increasing data integrity and user confidence.}
        \resumeItem{Implemented note-taking, pinning, and tracking with dynamic \textbf{MongoDB} schemas and modular frontend design.}
        \resumeItem{Improved deployment resilience via containerized \textbf{Docker} architecture, \textbf{CI/CD} pipelines, and automated testing workflows.}
        \resumeItem{Built accessible interface using \textbf{TailwindCSS} and \textbf{Framer Motion}, increasing UI engagement and clarity.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{GenAI Resume Pipeline}}{\href{https://github.com/altansaid/resume-updates}{GitHub}}{AI-Integrated Resume Optimization Workflow}{}
      \resumeItemListStart
        \resumeItem{Engineered event-driven resume pipeline in \textbf{n8n} with \textbf{Slack} integration and \textbf{OpenAI GPT} to auto-generate tailored LaTeX outputs.}
        \resumeItem{Automated GitHub file commits and versioning through \textbf{GitHub API} with layered validations and triggers.}
        \resumeItem{Achieved zero-failure completion using fallback logic and structured \textbf{JavaScript} transformations within custom code nodes.}
        \resumeItem{Cut manual resume prep time by automating metadata parsing, \textbf{base64} encoding, and strict LaTeX structure application.}
        \resumeItem{Ensured deterministic LaTeX results by blending AI inference with manual steps upon each \textbf{Slack} request.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
