\documentclass[letterpaper, 10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}

\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\usepackage[colorlinks=false, pdfborder={0 0 0}]{hyperref}
\usepackage[normalem]{ulem}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}



\setlength{\columnsep}{-1pt}

\usepackage[margin=1.4cm]{geometry}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.15in}
\addtolength{\textwidth}{0.3in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
\pdfgentounicode=1

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{0pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 




\begin{document}

%----------HEADING----------
\begin{center}
    {\Large \scshape Muhammed Said Altan} \\[2mm]
    \footnotesize
    (343) 988-3084 ~ 
    altansaid13@outlook.com ~ 
    \underline{\href{https://www.linkedin.com/in/altansaid/}{linkedin.com/in/altansaid}} ~ 
    \underline{\href{https://github.com/altansaid}{github.com/altansaid}} ~ 
    \underline{\href{https://saidaltan.com?utm_source=perceptivespace\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com}}
    \vspace{-10pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{April 2025}
      {Web Development and Internet Applications | Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
      \resumeItem{Relevant Coursework: Front-End Development(HTML, CSS, React), UI/UX Design, Object-Oriented Programming(JavaScript, C\#) Software Development Lifecycle, Algorithms for Computer Science, Network OS(Linux)} 

  \resumeSubHeadingListEnd
\vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Solace}{Sep 2024 -- Dec 2024}{Full Stack Web Developer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Engineered a responsive web interface utilizing \textbf{JavaScript/jQuery} that improved navigation efficiency in enterprise systems, reducing bounce rate by \textbf{42\%} through enhanced UI/UX design adhering to accessibility standards.}
\resumeItem{Enhanced CI/CD efficiency by resolving \textbf{Node.js} environment issues, diminishing failure rates by \textbf{80\%}, and stabilizing deployment pipelines.}

\resumeItem{Architected a modular internal microsite using \textbf{PHP, REST APIs, and Bootstrap}, facilitating a \textbf{50\% increase in user engagement} and enabling scalable content distribution across departments.}

\resumeItem{Optimized application scalability and security by integrating \textbf{RESTful services} and improving front-end component modularity using industry best practices for secure coding and performance.}

\resumeItem{Collaborated in Agile workflows, enhancing software reliability through backlog refinement and peer reviews, and reinforcing industry-standard practices in documentation and cross-functional team collaboration.}
\resumeItemListEnd

\resumeSubHeadingListEnd
  
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart


\resumeProjectHeading{\textbf{Real-Time Medical Exam Practice Platform}}
{\href{\detokenize{https://plab2practice.com/?utm_source=perceptivespace\&utm_medium=resume\&utm_campaign=job_application}}{Live Demo} $|$ \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
\vspace{-5pt}
\resumeItemListStart
    \resumeItem{Developed a cloud-scalable platform for \textbf{real-time medical exam preparation}, integrating \textbf{React, TypeScript, and WebSockets (STOMP)}, supporting \textbf{500+ active users} and enabling synchronized sessions.}
    
    \resumeItem{Deployed secure \textbf{Spring Boot RESTful microservices} with JWT authentication and over \textbf{25 API endpoints}, aligned with industry standards for maintainability and security.}
    
    \resumeItem{Created a responsive, WCAG-compliant UI using Material-UI and Tailwind CSS, ensuring universal accessibility and seamless performance across devices.}
    
    \resumeItem{Streamlined operations for \textbf{high-concurrency workloads} through PostgreSQL, \textbf{Docker}, and robust CI/CD integrations, supporting reliable cloud deployment.}
\resumeItemListEnd



\resumeSubHeadingListStart
\resumeProjectHeading{\textbf{AI-Powered Interview Preparation App}}
{\href{https://interviewcoach-ai.vercel.app}{Live Demo} $|$ \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}

\resumeItemListStart
    \resumeItem{Implemented a dynamic \textbf{full-stack platform} using \textbf{React 19 + TailwindCSS} and \textbf{Node.js/Express + MongoDB}, integrating AI to generate customized interview questions.}
    
    \resumeItem{Implemented robust authentication and role-based access using \textbf{JWT, Google OAuth, bcrypt}, ensuring secure and compliant user interactions.}
    
    \resumeItem{Enhanced system reliability with comprehensive \textbf{unit/integration testing}, establishing CI/CD pipelines for seamless cloud deployment.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%-----------Leadership-----------
\section{Leadership Experience}

\resumeSubHeadingListStart

\resumeSubheading
  {\href{https://www.bodyblissliz.com/}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
  {Project Lead \& Full Stack Web Developer (Capstone Project)}{Ottawa, ON}
  \vspace{1pt}
  \resumeItemListStart
     \resumeItem{Spearheaded a team to redesign a business website, implementing a responsive and accessible UI that enhanced mobile usability and elevated customer engagement.}
    \resumeItem{Partnered with clients to iteratively refine and implement features, significantly optimizing user experience and satisfaction.}
  \resumeItemListEnd
\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------

\section{Technical Skills}
\resumeItemListStart
  \resumeItem{\textbf{Languages:} JavaScript, TypeScript, Java, C{\#}, SQL, HTML5, CSS3}
  \resumeItem{\textbf{Front-End:} React, Redux, TailwindCSS, Server-Side Rendering, Responsive \& Accessible Design (WCAG)}
  \resumeItem{\textbf{Back-End \& Cloud:} Python, Django, RESTful APIs, JWT/OAuth, Docker, Git, AWS}
  \resumeItem{\textbf{Quality \& Practices:} Scalable Data APIs, Unit Testing (Jest, JUnit), Agile/Scrum, CI/CD Pipelines}
\resumeItemListEnd




\resumeSubHeadingListEnd
\end{document}