\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{JavaScript}/\textbf{jQuery} plugin for Table of Contents across portals, cutting navigation time and bounce rate by \textbf{42\%}.}
        \resumeItem{Resolved \textbf{Node.js} versioning issues in \textbf{CI/CD} pipelines to reduce build failures by \textbf{80\%} and improve deployment reliability.}
        \resumeItem{Built employee microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs} to improve engagement by \textbf{50\%} via modular, editable content workflows.}
        \resumeItem{Increased SEO scores to \textbf{90+} on all pages by fixing Lighthouse issues and enforcing accessibility best practices.}
        \resumeItem{Standardized UI/UX elements across platforms by designing interfaces in \textbf{Figma}, \textbf{Adobe Photoshop}, and \textbf{Illustrator}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built exam simulation tool supporting \textbf{500+ users} using \textbf{React} and \textbf{WebSockets} with live feedback and synchronized session states.}
        \resumeItem{Developed \textbf{JWT}-secured \textbf{Spring Boot} microservices with \textbf{60+ endpoints} and modular \textbf{REST API} flows for role-based scenarios.}
        \resumeItem{Optimized concurrency and schema workflow using \textbf{PostgreSQL}, Docker orchestration, and \textbf{Flyway}-based versioned migrations.}
        \resumeItem{Deployed full-stack system on \textbf{Vercel} and \textbf{Render} with scalable architecture and production-grade performance.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack \textbf{React}/\textbf{Node.js} app using \textbf{Gemini AI APIs} to generate tailored interview questions based on user roles.}
        \resumeItem{Implemented secure access control via \textbf{JWT} authentication and \textbf{Google OAuth} for seamless role-based routing.}
        \resumeItem{Enhanced accessibility using WCAG-compliant \textbf{TailwindCSS} layouts and interactive modal flows.}
        \resumeItem{Containerized platform with automated \textbf{CI/CD} testing for scalable and repeatable production deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Restaurant Review Management System}}{\href{https://github.com/altansaid/restaurantreviewmanagementsystem}{GitHub}}{Full-Stack Review Platform}{}
      \resumeItemListStart
        \resumeItem{Implemented modular \textbf{ASP.NET Core MVC} backend with layered validation, authentication, and centralized error handling.}
        \resumeItem{Designed responsive UI in \textbf{React} using Hooks and \textbf{Bootstrap 5} to support dynamic user review submissions.}
        \resumeItem{Connected SQL-based storage with robust CRUD operations for managing user reviews and restaurant metadata.}
        \resumeItem{Added session-aware routing and dynamic fields to capture and respond to live feedback data in real time.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}