\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} plugin for Table of Contents, reducing bounce rate by \textbf{42\%} and improving navigation flow on enterprise documentation sites.}
        \resumeItem{Resolved \textbf{Node.js} version conflicts in \textbf{CI/CD} pipeline, decreasing build failures by \textbf{80\%} and ensuring consistent automated deployments.}
        \resumeItem{Built modular employee microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing internal engagement by \textbf{50\%} through streamlined information delivery.}
        \resumeItem{Boosted SEO and accessibility scores to \textbf{90+} across internal portals by auditing with \textbf{Lighthouse} and resolving critical performance issues.}
        \resumeItem{Standardized UI/UX across internal tools using \textbf{Figma} mockups and \textbf{Adobe} assets, aligning interfaces with refreshed brand guidelines.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Created real-time practice system for \textbf{500+ users} using \textbf{React}, \textbf{Spring Boot}, and \textbf{WebSockets} to simulate exam scenarios with structured roleplay.}
        \resumeItem{Implemented role-based access using \textbf{JWT} and \textbf{Spring Security} to secure Doctor, Patient, and Observer actions based on user types.}
        \resumeItem{Optimized backend responsiveness to below \textbf{200ms} latency using \textbf{PostgreSQL}, \textbf{Flyway} migrations, and \textbf{Docker} containerization.}
        \resumeItem{Configured seamless CI deployment on \textbf{Render} and \textbf{Vercel} with custom domains and hot reloading for uninterrupted user experience.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Developed custom \textbf{MERN} stack application integrating \textbf{Gemini AI} to auto-generate behavioral and technical interview questions per user profile.}
        \resumeItem{Enabled password resets and multi-method login with secure \textbf{JWT}, \textbf{Google OAuth}, and encrypted store using \textbf{bcrypt}.}
        \resumeItem{Built \textbf{RESTful APIs} with note pinning, image uploads using \textbf{Multer}, and dynamic progress tracking to enhance preparation workflow.}
        \resumeItem{Automated testing and deployment on \textbf{Vercel} with integrated \textbf{CI/CD pipelines} to maintain stability after each commit.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{} {AI-Integrated Resume Optimization Pipeline}{}
      \resumeItemListStart
        \resumeItem{Designed intelligent workflow in \textbf{n8n} that parses job posts from Slack and generates custom \textbf{LaTeX} resumes using \textbf{OpenAI} large language models.}
        \resumeItem{Synchronized \textbf{HTTP}, \textbf{GitHub API}, and JavaScript nodes to serialize resume content and commit job-matched versions automatically.}
        \resumeItem{Implemented strict validation, versioning, and recovery logic in \textbf{LaTeX} pipeline to maintain \textbf{zero-failure} generation across multiple resume variants.}
        \resumeItem{Eliminated manual tailoring by \textbf{100\%} by leveraging contextual \textbf{GenAI} prompts for high-fidelity, job-aware resume drafts.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}
