\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS readability
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=redhat\&utm_medium=resume\&utm_campaign=job_application}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Engineered and launched a reusable \textbf{JavaScript/jQuery} Table of Contents plugin for enterprise platforms, improving navigation efficiency by \textbf{42\%} through streamlined code and advanced caching mechanisms.}
        \resumeItem{Diagnosed and corrected \textbf{Node.js} environment mismatches, reducing \textbf{CI/CD} pipeline failures by \textbf{80\%} by optimizing configurations and updating dependencies.}
        \resumeItem{Built and maintained an internal employee engagement microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, boosting participation by \textbf{50\%} by enhancing user interface and functionality.}
        \resumeItem{Enhanced full-stack development by integrating \textbf{RESTful services}, optimizing \textbf{React} components, and reinforcing security through \textbf{OWASP} best practices and thorough testing.}
        \resumeItem{Facilitated \textbf{Agile sprints} with global teams, improving process efficiency by conducting effective backlog refinement, peer reviews, and streamlining \textbf{CI/CD} workflows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com?utm_source=redhat\&utm_medium=resume\&utm_campaign=job_application}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Developed a scalable real-time platform supporting \textbf{500+ users} for medical prep using \textbf{React}, \textbf{WebSockets}, and \textbf{Spring Boot}, enabling enhanced practice sessions through live collaboration.}
        \resumeItem{Built secure \textbf{microservices} architecture with \textbf{JWT authentication} and \textbf{RESTful APIs}, maintaining \textbf{25+ endpoints} by employing modular design and rigorous testing.}
        \resumeItem{Optimized concurrency with \textbf{PostgreSQL} and \textbf{Docker}, achieving stable performance by streamlining queries and automating deployments.}
        \resumeItem{Designed accessible UI with \textbf{TailwindCSS}, conforming to WCAG standards by implementing responsive elements and intuitive navigation.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered an innovative \textbf{MERN} stack platform using \textbf{React} and \textbf{Node.js}, dynamically generating questions via \textbf{Gemini AI APIs} for comprehensive interview preparation experiences.}
        \resumeItem{Implemented secure \textbf{authentication} and role-based access control, safeguarding user data by employing \textbf{OAuth 2.0} standards.}
        \resumeItem{Prepared deployment-ready architecture with thorough \textbf{unit testing}, leveraging \textbf{CI/CD pipelines} and containerized environments for streamlined operation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------LEADERSHIP-----------------
\section{Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.bodyblissliz.com}{Bodyblissliz}}{Jan 2025 -- Apr 2025}
      {Project Lead \& Full Stack Web Developer (Capstone)}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Directed a 3-member team in revamping a client's website, achieving a fully responsive UI that boosted mobile usability by \textbf{35\%} through modern design and efficient coding practices.}
        \resumeItem{Partnered with clients to iteratively refine design, incorporating feedback to enhance user satisfaction and streamline interaction processes through focused testing and adjustments.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

%-------------------------------------------
\end{document}