\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Muhammed Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript}/\textbf{jQuery} plugin enhancing navigation across enterprise platforms, cutting bounce rates by \textbf{42\%} through improved link tracking and behavior analysis.}
        \resumeItem{Boosted Lighthouse scores to \textbf{90+} by resolving SEO violations and applying accessible \textbf{UI} updates that aligned with \textbf{AODA} compliance standards.}
        \resumeItem{Engineered modular \textbf{PHP} microsite using \textbf{REST APIs} and \textbf{Bootstrap}, increasing employee interaction by \textbf{50\%} through dynamic content delivery and reusable components.}
        \resumeItem{Eliminated \textbf{80\%} \textbf{CI/CD} failures by aligning \textbf{Node.js} versions and refining pipeline scripts to stabilize deployment environments.}
        \resumeItem{Unified cross-platform \textbf{UI} by synchronizing design assets from \textbf{Figma}, \textbf{Photoshop}, and \textbf{Illustrator} in agile sprint reviews.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built role-based \textbf{React} interface with \textbf{WebSockets} and \textbf{Spring Boot}, enabling real-time simulation sessions for \textbf{500+ users} across multiple user tiers globally.}
        \resumeItem{Designed \textbf{RESTful microservices} with \textbf{60+} endpoints in \textbf{Spring Boot}, improving modularity and reducing response latency under high concurrency.}
        \resumeItem{Secured platform access using \textbf{JWT} authorization, regulating permissions for Doctors, Patients, and Observers during active sessions.}
        \resumeItem{Optimized deployment flow with \textbf{Docker}, \textbf{PostgreSQL}, and \textbf{Flyway}, integrating \textbf{CI/CD} pipelines on \textbf{Render} and \textbf{Vercel}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview Preparation App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Developed full-stack \textbf{MERN} application using \textbf{Gemini AI APIs} to generate role-specific interview questions and explanatory feedback dynamically.}
        \resumeItem{Implemented secure \textbf{JWT} and \textbf{Google OAuth} authentication with encrypted sessions, route protection, and password recovery flows.}
        \resumeItem{Enabled image uploads via \textbf{Multer}, streamlining visual feedback exchange between candidates and reviewers.}
        \resumeItem{Delivered accessible, responsive interface with \textbf{TailwindCSS} and \textbf{Framer Motion}, conforming to \textbf{WCAG} and enhancing user interaction.}
      \resumeItemListEnd

  
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, TypeScript, C\#, SQL, HTML5, CSS3}
    \resumeItem{\textbf{Front-End}}{React, Redux, TailwindCSS, Material UI, WebSockets, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Back-End \& Cloud}}{Spring Boot, Node.js, RESTful APIs, JWT/OAuth, Docker, Git, Linux, Azure \& GCP}
    \resumeItem{\textbf{Quality \& Practices}}{JUnit 5, Jest, React Testing Library, CI/CD Pipelines, Agile/Scrum, Code Reviews}
  \resumeItemListEnd

\end{document}
