\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack \textbf{Go} and \textbf{React} SaaS integrating retail APIs, saving users \textbf{10--20+ hours/week} on product sourcing through automated analysis.}
        \resumeItem{Built concurrent \textbf{Go} microservices scraping \textbf{500+ products/hour}, using anti-bot headers and retries to ensure consistent data yield in production.}
        \resumeItem{Reduced validation workload by \textbf{80\%} via \textbf{OpenAI GPT}-powered normalization pipeline standardizing input for reliable profit estimation.}
        \resumeItem{Implemented tokenized \textbf{JWT} access, request throttling, and \textbf{Stripe} billing flow to preserve \textbf{PCI-compliant} security across all APIs.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} plugin improving technical doc navigation speed and lowering bounce rate by \textbf{42\%} across knowledge base pages.}
        \resumeItem{Resolved \textbf{Node.js CI/CD} versioning conflicts by refactoring pipelines, decreasing build failure rate by \textbf{80\%} across automated releases.}
        \resumeItem{Deployed internal microsite via \textbf{PHP} and \textbf{Bootstrap}, increasing cross-department engagement contributions by \textbf{50\%}.}
        \resumeItem{Elevated Lighthouse metrics by optimizing site \textbf{SEO} and accessibility, maintaining consistent score of \textbf{90+}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Engineered responsive \textbf{Spring Boot + React} app for \textbf{500+ users} enabling live collaboration with \textbf{WebSockets} maintaining sub-\textbf{200ms} latency.}
        \resumeItem{Built \textbf{60+ REST} endpoints with \textbf{Spring Security} using role-based logic and encrypted \textbf{JWT} authentication.}
        \resumeItem{Configured deployment stack with \textbf{Docker}, \textbf{PostgreSQL}, and \textbf{CI/CD}, deploying on \textbf{Render} and \textbf{Vercel}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app/}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {MERN-based AI Interview Preparation Platform}{}
      \resumeItemListStart
        \resumeItem{Built full-stack \textbf{MERN} app leveraging \textbf{Gemini API} to dynamically generate custom interview questions per candidate profile.}
        \resumeItem{Hardened platform with \textbf{JWT}, \textbf{Google OAuth}, bcrypt hashing, and secure password reset flows.}
        \resumeItem{Designed responsive interface using \textbf{TailwindCSS} with pinning logic and automatic \textbf{CI/CD} deployment routines.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
        \resumeItem{Built automated pipeline in \textbf{n8n} integrating \textbf{Slack}, \textbf{OpenAI GPT}, and \textbf{GitHub} to generate role-specific resumes.}
        \resumeItem{Automated delivery of validated \textbf{LaTeX} resumes in under \textbf{30 seconds} using incremental build and commit strategy.}
        \resumeItem{Maintained artifact integrity using multi-layer fallbacks and validation checks across all processing stages.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}