\documentclass[letterpaper, 10pt]{article}
\usepackage{resume} % Assume this package has been defined with necessary format

\begin{document}

% Header
\begin{center}
    {\Large \textbf{Muhammed Said Altan}} \\
    Ottawa, ON, Canada \\
    \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} $\mid$ \href{https://saidaltan.com}{Portfolio} \\
    \href{https://github.com/altansaid}{Github} $\mid$ \href{https://linkedin.com/in/saidaltan}{LinkedIn}
\end{center}

% Education
\section{Education}
\resumeSubheading{Diploma in Web Development and Internet Applications}{Algonquin College, Ottawa, Canada \qquad Apr 2025}

% Work Experience
\section{Experience}
\resumeSubheading{Web Developer Intern}{Solace, Ottawa, Canada \qquad Sep 2024 -- Dec 2024}
\resumeItemListStart
    \resumeItem{Enhanced SEO performance and accessibility by addressing audit findings	which improved scores to consistently exceed 90+ benchmarks.}
    \resumeItem{Developed and deployed a JavaScript/jQuery Table of Contents plugin integrated into enterprise knowledge bases, improving navigation speed and reducing bounce rate by 42%.}
    \resumeItem{Resolved Node.js environment mismatch issues, reducing build and deployment failures by 80% in CI/CD pipeline.}
    \resumeItem{Led the development of an internal employee engagement microsite using PHP, REST APIs, and Bootstrap, resulting in a 50\% increase in participation and enabling content reuse.}
    \resumeItem{Contributed to full-stack development by integrating RESTful services with frontend components.}
    \resumeItem{Collaborated with global teams in Agile sprints, participating in peer code reviews and CI/CD workflows.}
    \resumeItem{Created and improved UI/UX designs using design tools, enhancing the visual identity of internal sites.}
\resumeItemListEnd

% Projects
\section{Projects}
\resumeSubheading{PLAB2 Practice Platform}{\href{https://plab2practice.com}{plab2practice.com} $\mid$ \href{https://github.com/altansaid/plab2projectnew}{Github}}
\resumeItemListStart
    \resumeItem{Built a real-time collaborative platform for medical exam preparation with roles for Doctor, Patient, and Observer in live sessions, enabling structured and randomized clinical practices.}
    \resumeItem{Developed secure user registration and authentication with JWT, role-based access control, and deployed scalable Spring Boot microservices.}
    \resumeItem{Designed a responsive front-end with React, TypeScript, and Tailwind CSS, supporting accessibility standards, and integrated real-time synchronized features via WebSockets.}
\resumeItemListEnd

% Technical Skills
\section{Technical Skills}
\resumeSubItem{Languages}{JavaScript, TypeScript, Java, C\#, PHP, SQL, HTML5, CSS3}
\resumeSubItem{Frontend}{React, Redux, TailwindCSS, Material UI, Bootstrap, Responsive Design, WCAG}
\resumeSubItem{Backend}{Spring Boot, Node.js, ASP.NET Core, Laravel, Livewire, REST APIs, JWT/OAuth}
\resumeSubItem{Databases}{PostgreSQL, MySQL, MongoDB}
\resumeSubItem{Tools}{Docker, Git, Linux CLI, NVM, Homebrew}
\resumeSubItem{Cloud}{Render, Vercel, Netlify, Google Cloud Platform, Supabase}
\resumeSubItem{Practices}{Agile/Scrum, CI/CD, Unit Testing (Jest, JUnit), Clean Architecture, Code Reviews}

\end{document}