\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack \textbf{React}+\textbf{Go} SaaS platform reducing product sourcing time by \textbf{10--20 hours/week} through real-time arbitrage analytics across e-commerce marketplaces.}
        \resumeItem{Implemented \textbf{Go} microservices scraping \textbf{500+ products/hour} with retry logic, rate limiting, and anti-bot defenses to ensure robust and consistent API performance.}
        \resumeItem{Developed \textbf{OpenAI}-driven profit engine resolving data inconsistencies and normalizing units, decreasing manual review workload by over \textbf{80\%}.}
        \resumeItem{Deployed scalable infrastructure using \textbf{Firebase}, \textbf{Docker}, and \textbf{Google Cloud}, maintaining \textbf{99.9\%} uptime with real-time \textbf{React} dashboard.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin improving knowledge base retention and decreasing bounce rates by \textbf{42\%}.}
        \resumeItem{Boosted SEO and Lighthouse scores above \textbf{90/100} by restructuring DOM hierarchies and optimizing accessibility and asset loading.}
        \resumeItem{Developed internal microsite with \textbf{PHP}+\textbf{Bootstrap} and \textbf{REST APIs}, increasing user engagement by \textbf{50\%} through modular content reuse.}
        \resumeItem{Resolved cross-env \textbf{CI/CD} pipeline mismatches, reducing deployment failures by \textbf{80\%} through staged build validations.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{React}+\textbf{Spring Boot} platform supporting WebSocket sync under \textbf{200ms} for \textbf{500+ users} in interactive medical exam role-play simulations.}
        \resumeItem{Implemented cloud-deployable system using \textbf{Docker} with \textbf{JWT}-secured \textbf{REST APIs} across Render and Vercel.}
        \resumeItem{Created 60+ endpoints and normalized \textbf{PostgreSQL} schema with \textbf{Flyway} versioning to ensure scalable backend operations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{}{Live Demo} | \href{https://github.com/altansaid/resume-updates}{GitHub}}
      {Automated Resume Generation Pipeline}{}
      \resumeItemListStart
        \resumeItem{Engineered event-driven \textbf{n8n} pipeline connecting \textbf{Slack}, \textbf{OpenAI}, and \textbf{GitHub} to automate tailored resume generation and delivery.}
        \resumeItem{Created validation framework verifying \textbf{LaTeX} structure, encoding, and syntax for commit-stage error prevention.}
        \resumeItem{Optimized concurrency and catch blocks, enabling reliable output with \textbf{zero pipeline failures}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} JavaScript (ES6+), TypeScript, Go, Python, SQL}
    \resumeItem{\textbf{Frameworks \& Tools:} React, Node.js, Express, Spring Boot, Docker, PostgreSQL, GitHub Actions}
    \resumeItem{\textbf{Other:} WordPress (Custom Plugins), REST APIs, Agile/Scrum, Figma, SEO Optimization, CI/CD}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}