\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected \textbf{Go} microservices and containerized on \textbf{Docker}/\textbf{Google Cloud Run}, boosting data throughput \textbf{35\%} and ensuring \textbf{99.9\%} uptime across marketplaces.}
        \resumeItem{Implemented concurrent scraping with retry, caching, and rate limiting, cutting failed API calls \textbf{40\%} and processing \textbf{500+} products/hour per marketplace using \textbf{Go}.}
        \resumeItem{Delivered responsive \textbf{React} UI with debounced queries under \textbf{350ms} and dynamic filters, accelerating user decisions and CSV exports.}
        \resumeItem{Led design and code reviews, enforcing clean, testable patterns and secure \textbf{REST} practices across services.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{PHP}/\textbf{JavaScript} WordPress components, improving navigation and reducing bounce rate \textbf{42\%} across enterprise knowledge bases.}
        \resumeItem{Raised Lighthouse performance and accessibility to \textbf{90+} by optimizing SEO structure, images, and scripts with \textbf{JavaScript}.}
        \resumeItem{Launched engagement microsite via \textbf{PHP} and \textbf{REST} APIs, increasing participation \textbf{50\%} and enabling modular content reuse.}
        \resumeItem{Resolved Node.js CI/CD environment mismatches, reducing build failures \textbf{80\%} and stabilizing deployments with \textbf{GitHub Actions}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time role-play for \textbf{500+} users using \textbf{React}, \textbf{Spring Boot}, \textbf{WebSockets}; maintained sync latency under \textbf{200ms}.}
        \resumeItem{Exposed \textbf{60+} REST endpoints with \textbf{JWT} auth and role-based access on \textbf{PostgreSQL}, improving request efficiency and security.}
        \resumeItem{Containerized backend with \textbf{Docker} and Flyway migrations; deployed on \textbf{Render}/\textbf{Vercel} for repeatable, scalable releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Gemini AI} in \textbf{MERN} stack to auto-generate interview questions, eliminating manual creation and enabling realistic mock sessions.}
        \resumeItem{Secured authentication with \textbf{JWT} and \textbf{Google OAuth}; added password reset and file handling for reliable user flows.}
        \resumeItem{Automated testing and CI/CD via \textbf{GitHub Actions}, delivering stable releases and faster deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: Go, Python, PHP, JavaScript (ES6+), TypeScript, Java, SQL}
    \resumeItem{Frameworks \& Tools: React, Node.js, Express, Spring Boot, Docker, PostgreSQL, Firebase, Firestore, Google Cloud Run, GitHub Actions, WordPress}
    \resumeItem{Other: REST APIs, JWT, OAuth, WebSockets, CI/CD}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}