\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Shipped end-to-end SaaS features reducing discovery time by \textbf{10-20 hours/week} using \textbf{React}, \textbf{TypeScript}, and \textbf{Redux-Saga}, delivering revenue-driving dashboards and filters.}
        \resumeItem{Engineered concurrent \textbf{Go} microservices scraping \textbf{500+ products/hour} with rate limiting and retries, boosting reliability by \textbf{40\%} and API throughput by \textbf{35\%}.}
        \resumeItem{Implemented AI profit analysis reducing manual validation by \textbf{80\%} via \textbf{OpenAI}, normalizing pack quantities across marketplaces for accurate margins.}
        \resumeItem{Delivered secure payments and auth with \textbf{Stripe}, \textbf{Firebase Auth}, CORS whitelisting, and rate limiting, achieving \textbf{99.9\%} uptime on \textbf{Google Cloud Run}.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{JavaScript}/\textbf{jQuery} Table of Contents plugin improving navigation and reducing bounce rate by \textbf{42\%} across enterprise knowledge bases.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility to \textbf{90+} by optimizing SEO, scripts, and images using \textbf{PHP} and \textbf{JavaScript}.}
        \resumeItem{Built internal microsite with \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee engagement by \textbf{50\%} and enabling modular content reuse.}
        \resumeItem{Resolved \textbf{Node.js} \textbf{CI/CD} environment mismatches, cutting build failures by \textbf{80\%}, and partnered with designers and PMs in \textbf{Agile} sprints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time platform serving \textbf{500+ users} with \textbf{React}, \textbf{TypeScript}, and \textbf{WebSockets}, enabling role-play sessions under \textbf{200ms} latency.}
        \resumeItem{Designed secure \textbf{Spring Boot} \textbf{REST} APIs with \textbf{JWT} and RBAC, deployed via \textbf{Docker} for cloud scalability.}
        \resumeItem{Optimized \textbf{PostgreSQL} with indexed queries and Flyway migrations, sustaining \textbf{60+} endpoints and stable production traffic.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Built end-to-end \textbf{MERN} app integrating \textbf{Gemini AI} to generate tailored questions, increasing practice relevance and completion rate.}
        \resumeItem{Secured auth with \textbf{JWT}, \textbf{Google OAuth}, \textbf{bcrypt}, and email resets, protecting accounts and simplifying onboarding.}
        \resumeItem{Ensured reliable releases via automated tests and \textbf{CI/CD} using \textbf{GitHub Actions} and containerized configs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: JavaScript (ES6+), TypeScript, Java, Go, Python, PHP, SQL}
    \resumeItem{Frameworks \& Tools: React, Node.js, Express, Redux, Spring Boot, Docker, Firebase, Firestore, PostgreSQL, MongoDB, GitHub Actions}
    \resumeItem{Other: REST APIs, End-to-end development, WebSockets, Authentication (JWT, OAuth), Performance Optimization, Accessibility, SEO, CI/CD, Agile/Scrum}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}