\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered platform cutting product discovery time by \textbf{10-20 hours/week} for users using real-time multi-marketplace analysis with \textbf{React} frontend and \textbf{Go} microservices.}
        \resumeItem{Deployed \textbf{Go} microservices scraping \textbf{500+ products/hour} per marketplace, implementing rate limiting and retries to ensure reliable high-throughput ingestion.}
        \resumeItem{Optimized \textbf{Firestore} queries to deliver \textbf{70\%} faster retrieval across \textbf{10,000+} products by implementing indexed pagination and lazy loading.}
        \resumeItem{Integrated \textbf{Stripe}, \textbf{Keepa}, and \textbf{Amazon SP-API} to achieve \textbf{95\%+} profit accuracy and send automated marketing emails with \textbf{45\%} open rates.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin for enterprise knowledge bases, improving navigation speed and reducing bounce rate by \textbf{42\%}.}
        \resumeItem{Improved \textbf{SEO} and accessibility by fixing \textbf{Lighthouse} issues, increasing performance and accessibility scores to \textbf{90+} across \textbf{WordPress} systems.}
        \resumeItem{Built internal microsite with \textbf{PHP} and \textbf{REST APIs}, increasing employee participation by \textbf{50\%} and enabling modular content reuse.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches, reducing \textbf{CI/CD} build and deployment failures by \textbf{80\%} through tooling and regression detection.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered real-time collaborative platform serving \textbf{500+} active users using \textbf{WebSockets} and role-based sessions for Doctor, Patient, and Observer workflows.}
        \resumeItem{Secured authentication with \textbf{JWT} and \textbf{Spring Security}, reducing session issues and enforcing role-based access across microservices.}
        \resumeItem{Achieved sub-\textbf{200ms} real-time sync for \textbf{500+} users by optimizing \textbf{PostgreSQL} queries and Dockerized deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Architected modular \textbf{n8n} workflow delivering tailored resumes within \textbf{30 seconds} from a single \textbf{Slack} trigger by sequencing AI, validation, and persistence nodes.}
    \resumeItem{Orchestrated \textbf{OpenAI} inference and validation to produce X--Y--Z statements and enforce LaTeX-safe output, maintaining \textbf{0\%} invalid commits with fault-tolerant fallbacks.}
    \resumeItem{Committed validated \textbf{LaTeX} resumes via \textbf{GitHub} REST API, achieving \textbf{100\%} version traceability and atomic persistence.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}