\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack SaaS platform accelerating product sourcing by \textbf{10--20 hours/week} per user through real-time multi-marketplace analysis using \textbf{Go} microservices and \textbf{React} frontend.}
        \resumeItem{Built \textbf{Go} \textbf{microservices} scraping \textbf{500+ products/hour} per marketplace, implementing \textbf{rate limiting} and \textbf{retry logic} to ensure reliable concurrent ingestion.}
        \resumeItem{Integrated \textbf{Amazon SP-API}, \textbf{Keepa}, and \textbf{Stripe} to deliver \textbf{95\%+} accurate profit and \textbf{ROI} calculations for real-time decisioning.}
        \resumeItem{Optimized \textbf{Firestore} \textbf{indexed pagination} and \textbf{lazy loading}, improving data retrieval speed by \textbf{70\%} for datasets exceeding \textbf{10,000} products.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} Table of Contents plugin reducing bounce rate by \textbf{42\%} across enterprise knowledge bases by optimizing \textbf{DOM} updates and \textbf{CMS} integration.}
        \resumeItem{Improved performance and accessibility to exceed \textbf{90+ Lighthouse} scores for internal \textbf{WordPress} systems by resolving audits and implementing semantic \textbf{HTML} and \textbf{ARIA} attributes.}
        \resumeItem{Delivered internal employee engagement microsite increasing participation by \textbf{50\%} using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap} to enable modular content reuse.}
        \resumeItem{Reduced \textbf{Node.js} \textbf{CI/CD} build failures by \textbf{80\%} by resolving environment mismatches and adding \textbf{regression detection} tooling in Agile sprints.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered real-time platform supporting \textbf{500+ active users} with sub-\textbf{200ms} latency by implementing \textbf{WebSockets} and optimized backend \textbf{Spring Boot} \textbf{microservices}.}
        \resumeItem{Implemented \textbf{JWT}-secured authentication and \textbf{role-based access} with \textbf{Spring Security}, improving session reliability for timed consultations and feedback workflows.}
        \resumeItem{Deployed \textbf{Dockerized} services with \textbf{PostgreSQL} and \textbf{CI/CD} on \textbf{Render} and \textbf{Vercel}, enabling scalable production for cloud-ready users.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Architected modular \textbf{n8n} workflow producing validated resumes from \textbf{Slack} events within \textbf{30 seconds} by orchestrating trigger, data retrieval, \textbf{AI} inference, and validation nodes.}
    \resumeItem{Orchestrated \textbf{OpenAI GPT} inference to generate X--Y--Z achievement statements, enforcing multi-level \textbf{LaTeX} validation and achieving \textbf{0\%} invalid outputs before commit.}
    \resumeItem{Implemented authenticated \textbf{GitHub} commit operations to persist versioned \textbf{LaTeX} artifacts, ensuring \textbf{100\%} traceability and reproducible resume deliveries.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}