\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered responsive B2B analytics UI with \textbf{React}, \textbf{TypeScript}, \textbf{Redux-Saga}, achieving \textbf{<350ms} filtered queries and \textbf{99.9\%} uptime across sessions.}
        \resumeItem{Implemented component library with accessible patterns and \textbf{WCAG 2.1 AA}, lifting \textbf{Lighthouse} performance and accessibility scores to \textbf{95+} on modern browsers.}
        \resumeItem{Integrated \textbf{REST APIs} from \textbf{Go} microservices with error boundaries, retries, and caching, reducing failed API calls by \textbf{40\%} and improving resilience.}
        \resumeItem{Collaborated with design in \textbf{Agile} sprints to deliver pixel-perfect components, code reviews, and \textbf{CI/CD} via \textbf{GitHub Actions}, standardizing \textbf{Git} workflow and \textbf{Jira} tracking.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{WordPress} Table-of-Contents plugin using \textbf{PHP}, \textbf{JavaScript}, and \textbf{jQuery}, improving navigation speed and reducing bounce rate by \textbf{42\%} across knowledge bases.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} by optimizing \textbf{SEO} structure, images, and scripts with \textbf{Webpack} and \textbf{Babel} configurations.}
        \resumeItem{Launched employee microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing engagement by \textbf{50\%} and enabling reusable modules for multiple departments.}
        \resumeItem{Resolved \textbf{Node.js} \textbf{CI/CD} environment mismatches, reducing build failures by \textbf{80\%} and improving release consistency with \textbf{Git} workflows and \textbf{Jira}-managed \textbf{Agile} sprints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered real-time role-play for \textbf{500+} users with under \textbf{200ms} sync using \textbf{React}, \textbf{TypeScript}, \textbf{WebSocket} \textbf{STOMP}, and \textbf{Spring Boot}.}
        \resumeItem{Built \textbf{60+} \textbf{REST} endpoints with \textbf{JWT} auth and \textbf{PostgreSQL}, containerized via \textbf{Docker}, improving reliability and scalable deployments.}
        \resumeItem{Implemented accessible, responsive UI meeting \textbf{WCAG 2.1 AA} and \textbf{React Router} navigation, achieving \textbf{Lighthouse} \textbf{95+} across devices.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Built AI interview platform using \textbf{React} and \textbf{Node.js} with \textbf{Gemini API}, generating tailored questions in under \textbf{2s} per prompt.}
        \resumeItem{Implemented secure authentication with \textbf{JWT}, \textbf{Google OAuth}, and \textbf{bcrypt}, protecting \textbf{10+} routes and enabling token-based password reset.}
        \resumeItem{Set up \textbf{CI/CD} with \textbf{GitHub Actions} and \textbf{Docker}, reducing deployment time by \textbf{50\%} and ensuring consistent releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} JavaScript (ES6+), TypeScript, HTML5, CSS3, SQL, Go, Python}
    \resumeItem{\textbf{Frameworks \& Tools:} React, Redux, React Router, Node.js, Express, Spring Boot, Webpack, Babel, Docker, PostgreSQL, Git, GitHub Actions, Jira}
    \resumeItem{\textbf{Other:} CMS (WordPress, Laravel/Livewire), REST APIs, Accessibility (WCAG 2.1), SEO Optimization, Cross-browser Testing, CI/CD, Agile/Scrum, Figma}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}