\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=cheil\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{ArbitHub}}{Jul 2025 -- Present}
      {Front-End Web Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{React} \textbf{TypeScript} dashboards, cutting query latency to \textbf{<350ms} by implementing debounced searches, \textbf{Redux} state, and dynamic filters across \textbf{20+} parameters.}
        \resumeItem{Optimized \textbf{Firestore} queries with indexed pagination and lazy loading, improving data retrieval speed by \textbf{70\%} for datasets exceeding \textbf{10,000} products across multi-tenant views.}
        \resumeItem{Achieved \textbf{99.9\%} uptime in production by deploying \textbf{Docker}-containerized services on \textbf{Google Cloud} with automated scaling and proactive SLO monitoring.}
        \resumeItem{Implemented secure \textbf{authentication}, \textbf{CORS} whitelisting, and rate-limiting across \textbf{APIs}, reducing unauthorized requests by \textbf{60\%} and safeguarding \textbf{Stripe} checkout flows.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer Intern (CMS Publishing \& Optimization)}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{WordPress} \textbf{JavaScript}/\textbf{jQuery} Table of Contents block, reducing content bounce rate by \textbf{42\%} by improving in-page navigation across enterprise knowledge bases.}
        \resumeItem{Elevated \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} by fixing semantic HTML, contrast, and asset delivery, improving \textbf{SEO} and user experience across \textbf{WordPress Multisite}.}
        \resumeItem{Delivered internal microsite with \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing employee participation by \textbf{50\%} by enabling modular content reuse and responsive components.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches in \textbf{CI/CD}, cutting build and deployment failures by \textbf{80\%} through version pinning, cache busting, and pipeline validation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Enabled \textbf{500+ users} to practice collaboratively by building \textbf{React} \textbf{TypeScript} frontend with \textbf{WebSockets} (\textbf{STOMP}), sustaining \textbf{200+} concurrent sessions under \textbf{200ms} sync latency.}
        \resumeItem{Scaled services with \textbf{Spring Boot} microservices, \textbf{PostgreSQL}, and \textbf{Docker}, increasing throughput by \textbf{3x} by adding indexes, caching, and batched writes.}
        \resumeItem{Improved availability to \textbf{99.9\%} by deploying backend on \textbf{Render} and frontend on \textbf{Vercel}, with \textbf{CI/CD} and health checks for zero-downtime releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack \textbf{MERN} app with \textbf{React} and \textbf{Node.js}/\textbf{Express}, integrating \textbf{Gemini AI} to generate tailored questions, exposing \textbf{20+} secure \textbf{API} routes.}
        \resumeItem{Implemented \textbf{JWT} and \textbf{Google OAuth} with encrypted storage and \textbf{bcrypt}, securing \textbf{100\%} private endpoints and standardizing session management.}
        \resumeItem{Increased release reliability by \textbf{100\%} by implementing \textbf{CI/CD} with \textbf{Docker}, automated tests using \textbf{Jest} and \textbf{React Testing Library}, and environment-specific configs.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{HTML5, CSS3/Sass, JavaScript (ES6+), TypeScript, PHP, SQL, Java}
    \resumeItem{\textbf{Front-End}}{React, TailwindCSS, Bootstrap, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{CMS Tools}}{WordPress (Multisite, Themes, Plugins), Gutenberg, Elementor, WP-CLI}
    \resumeItem{\textbf{Design \& Collaboration}}{Figma, Photoshop, Adobe XD, Agile/Scrum, Version Control (Git)}
    \resumeItem{\textbf{Analytics \& Optimization}}{GA4, SEO, Google Tag Manager, Lighthouse, Performance Auditing}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}