\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered full-stack SaaS for online arbitrage, saving users \textbf{10-20 hours/week} via real-time analytics built with \textbf{JavaScript}, \textbf{React}, and \textbf{Go}.}
        \resumeItem{Built concurrent \textbf{Go} microservices with retry, rate limiting, and caching, processing \textbf{500+ products/hour} and cutting failed calls \textbf{40\%}.}
        \resumeItem{Optimized \textbf{Firestore} indexing and pagination, improving data retrieval speed \textbf{70\%} for datasets of \textbf{10,000+} records.}
        \resumeItem{Established \textbf{Git} workflows, automated \textbf{CI/CD}, and \textbf{Agile} practices, reducing deployment failures \textbf{80\%} and accelerating releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{WordPress} components with \textbf{PHP} and \textbf{JavaScript}, improving navigation speed and reducing bounce rate \textbf{42\%}; optimized \textbf{SQL} queries for content retrieval.}
        \resumeItem{Increased \textbf{Lighthouse} performance and accessibility to \textbf{90+} by refactoring scripts, images, and semantic \textbf{HTML}, enhancing \textbf{SEO}.}
        \resumeItem{Built internal microsite with \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, raising employee engagement \textbf{50\%}; enabled modular content reuse.}
        \resumeItem{Resolved \textbf{CI/CD} issues and improved \textbf{Git} workflows in \textbf{Agile} sprints, reducing deployment failures \textbf{80\%} and accelerating releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time role-play platform serving \textbf{500+} users using \textbf{React}, \textbf{Spring Boot}, and \textbf{WebSockets}, achieving sub-\textbf{200ms} sync.}
        \resumeItem{Designed \textbf{REST APIs} with \textbf{JWT} and role-based access; containerized with \textbf{Docker} and deployed to cloud.}
        \resumeItem{Optimized \textbf{PostgreSQL} schema and indexes via \textbf{Flyway}, improving query latency \textbf{45\%} and supporting concurrent sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Delivered AI interview prep app using \textbf{JavaScript}, \textbf{Node.js}, and \textbf{React}; generated tailored questions with \textbf{Gemini}, improving session quality \textbf{30\%}.}
        \resumeItem{Implemented secure auth with \textbf{JWT}, \textbf{Google OAuth}, and email reset; enforced validation and role-based access.}
        \resumeItem{Automated testing and \textbf{CI/CD} with \textbf{GitHub Actions}, reducing release errors \textbf{60\%} and accelerating deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} JavaScript (ES6+), TypeScript, PHP, C\#, Go, Java, Python, SQL}
    \resumeItem{\textbf{Frameworks \& Tools:} React, Node.js, Express, ASP.NET Core, Laravel, WordPress, Spring Boot, Docker, PostgreSQL, MySQL, Git, GitHub Actions}
    \resumeItem{\textbf{Other:} REST APIs, Agile/Scrum, CI/CD, Testing, Code Reviews, SEO Optimization, Figma}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}