\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built real-time analytics app, increasing data throughput by \textbf{35\%} with \textbf{React} UI optimizations and indexed pagination.}
        \resumeItem{Developed \textbf{Go} microservices and \textbf{REST} APIs with retry and caching, reducing failed calls by \textbf{40\%}.}
        \resumeItem{Integrated \textbf{OpenAI} for automated product matching, cutting manual validation time by \textbf{80\%}.}
        \resumeItem{Containerized and deployed services using \textbf{Docker} and \textbf{GitHub Actions} on \textbf{Google Cloud}, maintaining \textbf{99.9\%} uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{WordPress} components, reducing bounce rate by \textbf{42\%} and achieving \textbf{90+} Lighthouse using \textbf{PHP}, \textbf{JavaScript}, and \textbf{jQuery}.}
        \resumeItem{Optimized SEO, performance, and accessibility, raising scores above \textbf{90} via semantic \textbf{HTML5}, \textbf{CSS}, and image/script tuning.}
        \resumeItem{Resolved CI/CD issues, cutting deployment failures by \textbf{80\%} via \textbf{Node.js} environment fixes and \textbf{GitHub Actions} workflows.}
        \resumeItem{Delivered event microsite increasing participation by \textbf{50\%} using \textbf{PHP}, \textbf{REST APIs}, \textbf{Bootstrap}, and responsive components.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time practice platform for \textbf{500+} users with \textbf{React}, \textbf{TypeScript}, \textbf{Spring Boot}, and \textbf{WebSocket}, achieving sub-\textbf{200ms} sync latency.}
        \resumeItem{Delivered \textbf{60+} REST endpoints with \textbf{JWT} RBAC; improved consistency using \textbf{PostgreSQL} indexing and \textbf{Flyway} migrations.}
        \resumeItem{Deployed containerized services with \textbf{Docker} on \textbf{Render} and \textbf{Vercel}, enabling zero-downtime updates and scalable releases.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Integrated \textbf{Gemini AI} into \textbf{React}/\textbf{Node.js} app to generate tailored questions and feedback, enabling realistic mock interview sessions.}
        \resumeItem{Implemented secure auth with \textbf{Google OAuth}, \textbf{JWT}, and bcrypt resets, strengthening authentication and session continuity.}
        \resumeItem{Automated testing and CI/CD with \textbf{GitHub Actions} and containerized configs, ensuring stable releases and faster deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: JavaScript (ES6+), TypeScript, Go, Java, C\#, Python, SQL, HTML5, CSS3}
    \resumeItem{Frontend: React, Redux, Tailwind CSS, Material UI, Bootstrap, WebSocket}
    \resumeItem{Backend: Node.js, Express, Spring Boot, ASP.NET Core, REST APIs, JWT, OAuth2}
    \resumeItem{Databases: PostgreSQL, MongoDB, MySQL, Firestore}
    \resumeItem{Cloud \& DevOps: Docker, Git, GitHub Actions, Vercel, Render, Google Cloud Run}
    \resumeItem{CMS: WordPress (Custom Plugins), Gatsby}
    \resumeItem{Tooling: ESLint, Prettier, NVM, Linux CLI}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}
