\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Shipped full-stack SaaS with \textbf{React}+\textbf{Redux-Saga}, improving data throughput \textbf{35\%} and sub-\textbf{350ms} queries via indexed \textbf{Firestore} and debounced filters.}
        \resumeItem{Built concurrent \textbf{Go} microservices with rate limiting, retries, and caching, reducing failed API calls \textbf{40\%} and sustaining \textbf{500+} products/hour per marketplace.}
        \resumeItem{Implemented \textbf{OpenAI} GPT-driven product normalization, cutting manual validation time \textbf{80\%} and improving matching accuracy across marketplaces.}
        \resumeItem{Deployed containerized services on \textbf{Google Cloud Run} with \textbf{Docker}+\textbf{GitHub Actions}, achieving \textbf{99.9\%} uptime and enforcing \textbf{JWT}, \textbf{CORS} whitelisting, and rate limits.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript}/\textbf{jQuery} Table of Contents plugin, improving navigation speed and reducing bounce rate \textbf{42\%} across enterprise knowledge bases.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} by optimizing \textbf{HTML5}/\textbf{CSS3} structure, \textbf{ES6+} scripts, and image delivery.}
        \resumeItem{Built internal microsite with \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing employee participation \textbf{50\%} and enabling modular content reuse.}
        \resumeItem{Resolved \textbf{Node.js} \textbf{CI/CD} environment mismatches, cutting build failures \textbf{80\%} and standardizing version control with \textbf{Git} workflows.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time platform serving \textbf{500+} users with \textbf{React}+\textbf{TypeScript} and \textbf{WebSocket}, sustaining sub-\textbf{200ms} sync across collaborative sessions.}
        \resumeItem{Designed \textbf{Spring Boot} \textbf{REST APIs} with \textbf{JWT} auth and role-based access, enabling secure scenarios and feedback workflows.}
        \resumeItem{Containerized and deployed via \textbf{Docker} with \textbf{PostgreSQL} migrations, improving scalability and reliability under growing load.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Delivered full-stack MERN app using \textbf{React} and \textbf{Node.js}/\textbf{Express}, integrating \textbf{Gemini AI} to generate personalized interview questions and feedback.}
        \resumeItem{Implemented secure auth with \textbf{Google OAuth}, \textbf{JWT}, and password resets, increasing successful login rate \textbf{25\%} during beta by simplifying flows.}
        \resumeItem{Set up automated tests and \textbf{CI/CD} with \textbf{GitHub Actions}, reducing release time \textbf{40\%} and ensuring stable deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: TypeScript, JavaScript (ES6+), Java, Go, Python, SQL}
    \resumeItem{Frontend: React, Redux, Tailwind CSS, Material UI, Bootstrap, HTML5, CSS3, WebSocket, Responsive Design}
    \resumeItem{Backend: Node.js, Express, Spring Boot, REST APIs, JWT, OAuth}
    \resumeItem{Testing and Quality: Unit Testing, Integration Testing, Lighthouse, CI/CD}
    \resumeItem{Cloud and DevOps: Docker, GitHub Actions, Firebase, Firestore, Google Cloud Run, Vercel, Render}
    \resumeItem{Tools: Git, Linux/Unix CLI, Jira, Figma, SEO}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}