\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built full-stack \textbf{React}+\textbf{Go} application, increasing data throughput by \textbf{35\%} across marketplaces using \textbf{Firebase} and containers.}
        \resumeItem{Developed modular \textbf{Go} microservices with retry and caching, reducing failed API calls by \textbf{40\%} and scraping \textbf{500+} products/hour.}
        \resumeItem{Integrated \textbf{OpenAI} models for automated product matching, cutting manual validation time by \textbf{80\%} through data normalization.}
        \resumeItem{Engineered responsive \textbf{React}/\textbf{TypeScript} UI with \textbf{Redux-Saga}, under \textbf{350ms} debounced queries and CSV export for analysts.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable WordPress Table of Contents plugin, reducing bounce rate by \textbf{42\%} using \textbf{PHP} and \textbf{JavaScript}.}
        \resumeItem{Raised Lighthouse performance and accessibility scores to \textbf{90+/100} by optimizing scripts, images, and critical \textbf{CSS}.}
        \resumeItem{Built employee microsite increasing participation by \textbf{50\%} using \textbf{PHP}, \textbf{Bootstrap}, and REST APIs.}
        \resumeItem{Resolved Node.js CI environment mismatches, reducing build failures by \textbf{80\%} and stabilizing pipelines with \textbf{GitHub Actions}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built platform serving \textbf{500+} active users using \textbf{React}, \textbf{Spring Boot}, and \textbf{WebSockets}.}
        \resumeItem{Reduced synchronization latency to under \textbf{200ms} via STOMP message batching and session-state optimizations.}
        \resumeItem{Secured role-based APIs with \textbf{JWT} and deployed with \textbf{Docker} to cloud for scalable sessions.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Integrated \textbf{Gemini} AI to generate personalized interview prompts, improving practice realism for users.}
        \resumeItem{Implemented secure auth with \textbf{Google OAuth} and \textbf{JWT}, plus email password reset flows.}
        \resumeItem{Configured CI/CD and automated tests with \textbf{GitHub Actions} for reliable, fast deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} TypeScript, JavaScript (ES6+), HTML5, CSS3, Go, Python, SQL}
    \resumeItem{\textbf{Frontend:} React, Redux, WebSocket, Tailwind CSS, Material UI, Bootstrap}
    \resumeItem{\textbf{Backend \& APIs:} Node.js, Express, Spring Boot, JWT, Stripe API, RESTful APIs}
    \resumeItem{\textbf{Databases \& Cloud:} PostgreSQL, MongoDB, Firebase, Google Cloud Run, Render, Vercel}
    \resumeItem{\textbf{DevOps \& Tools:} Docker, GitHub Actions, Docker Compose, Git, CI/CD, Docker Hub}
    \resumeItem{\textbf{AI \& Integrations:} OpenAI, Gemini, Stripe API, SendGrid, Amazon SP-API}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}