\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack \textbf{React}+\textbf{TypeScript} app with \textbf{Go} services for real-time marketplace analytics, increasing data throughput \textbf{35\%} via indexed queries, batched fetches, and debounced client filters.}
        \resumeItem{Developed modular \textbf{Go} microservices with caching, retries, and circuit breakers, reducing failed API calls \textbf{40\%} and sustaining \textbf{500+} requests/min under load.}
        \resumeItem{Integrated \textbf{OpenAI} \textbf{LLM} APIs for product matching, cutting manual validation \textbf{80\%} and accelerating prototype-to-production handoffs.}
        \resumeItem{Shipped secure services on \textbf{Google Cloud} with \textbf{GitHub Actions} \textbf{CI/CD}, sustaining \textbf{99.9\%} uptime and driving \textbf{Agile} reviews, estimates, and documentation.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{JavaScript}/\textbf{jQuery} Table-of-Contents plugin, improving navigation speed and lowering bounce rate \textbf{42\%} across enterprise knowledge bases.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility to \textbf{90+} by optimizing \textbf{SEO} structure, scripts, and image handling.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches in \textbf{CI/CD}, reducing build and deployment failures \textbf{80\%} across environments.}
        \resumeItem{Delivered \textbf{PHP}-based event microsite via \textbf{REST} \textbf{APIs} and \textbf{Bootstrap}, increasing employee participation \textbf{50\%} while collaborating in \textbf{Agile} sprints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time PLAB2 platform serving \textbf{500+} users using \textbf{React}, \textbf{TypeScript}, and \textbf{WebSocket} sync with \textbf{Spring Boot} services.}
        \resumeItem{Reduced sync latency to \textbf{<200ms} by batching messages, optimizing session state, and indexing \textbf{PostgreSQL} queries.}
        \resumeItem{Secured APIs with \textbf{JWT} and deployed via \textbf{Docker} containers to cloud hosting, enabling reliable releases and role-based access control.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Gemini} \textbf{LLM} to generate personalized interview questions, reducing content authoring time \textbf{90\%} during mock sessions.}
        \resumeItem{Built secure authentication with \textbf{Google OAuth}, \textbf{JWT}, and email reset, hardening endpoints in \textbf{Node.js}/\textbf{Express}.}
        \resumeItem{Enabled automated testing and \textbf{CI/CD} with \textbf{GitHub Actions}, cutting release time \textbf{50\%} and stabilizing deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: TypeScript, JavaScript, Java, Python, Go, SQL}
    \resumeItem{Frameworks \& Tools: React, Node.js, Express, Spring Boot, Docker, PostgreSQL, WebSocket, GitHub Actions, Google Cloud}
    \resumeItem{Other: LLM APIs (OpenAI, Gemini), REST APIs, Agile/Scrum, CI/CD, WordPress (Custom Plugins), Figma, SEO Optimization}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}