\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected containerized \textbf{React}+\textbf{Go} SaaS on \textbf{Google Cloud Run} and \textbf{Firebase}, delivering \textbf{99.9\%} uptime and \textbf{35\%} higher data throughput.}
        \resumeItem{Built \textbf{Go} microservices with concurrency, rate limiting, retries, and caching, cutting failed API calls by \textbf{40\%} and processing \textbf{500+} products/hour.}
        \resumeItem{Implemented AI-driven profit analysis and product matching, reducing manual validation by \textbf{80\%} through \textbf{OpenAI} services and secure \textbf{JWT}-protected APIs.}
        \resumeItem{Set up \textbf{GitHub Actions} CI/CD, unit tests, and \textbf{Docker} builds, enabling gated PRs and repeatable releases aligned to standards.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{WordPress} components in \textbf{PHP}/\textbf{JavaScript}, raising \textbf{Lighthouse} performance and accessibility to \textbf{90+/100} across enterprise pages.}
        \resumeItem{Built an engagement microsite using \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee participation by \textbf{50\%}.}
        \resumeItem{Fixed \textbf{Node.js} CI/CD environment mismatches, cutting build and deployment failures by \textbf{80\%} and standardizing branching/versioning.}
        \resumeItem{Performed peer reviews, documented components, and triaged incidents, improving support responsiveness within Agile sprints.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered a real-time \textbf{React}+\textbf{Spring Boot} platform for \textbf{500+} users with \textbf{WebSockets}, achieving sub-\textbf{200ms} synchronization.}
        \resumeItem{Exposed \textbf{60+} REST endpoints with role-based \textbf{JWT} auth, \textbf{PostgreSQL}, and migrations for reliable data integrity.}
        \resumeItem{Containerized services with \textbf{Docker} and deployed on \textbf{Render}/\textbf{Vercel}, enabling reproducible builds and zero-downtime updates.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Built an interview coach using \textbf{React}+\textbf{Node.js}, integrating \textbf{Gemini AI} to generate personalized questions and feedback.}
        \resumeItem{Implemented secure authentication with \textbf{Google OAuth}, \textbf{JWT}, bcrypt, and email-based password resets to protect accounts.}
        \resumeItem{Established \textbf{GitHub Actions} pipelines and containerized configs for automated testing and reliable deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: TypeScript, JavaScript, Java, Go, Python, SQL, PHP}
    \resumeItem{Frameworks \& Tools: React, Redux, Node.js, Express, Spring Boot, WordPress, Docker, GitHub Actions, REST APIs, JWT, OAuth, Tailwind CSS, Git, Linux}
    \resumeItem{Platforms \& Databases: Firebase, Firestore, Google Cloud Run, Render, Vercel, PostgreSQL}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}