\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built \textbf{Go} microservices achieving \textbf{500+ products/hour} across marketplaces by implementing \textbf{rate limiting}, \textbf{retry} backoff, and async queues.}
        \resumeItem{Reduced manual validation time by \textbf{80\%} in profit analysis by integrating \textbf{OpenAI GPT-3.5} to normalize pack quantities and detect cross-market inconsistencies.}
        \resumeItem{Optimized \textbf{Firestore} with \textbf{indexed pagination} and caching, improving query latency by \textbf{70\%} and sustaining datasets of \textbf{10,000+} products.}
        \resumeItem{Deployed containerized \textbf{Go} services on \textbf{Google Cloud} and \textbf{Firebase Functions}, achieving \textbf{99.9\%} uptime with \textbf{autoscaling}, centralized logging, and health checks.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed a reusable \textbf{JavaScript/jQuery} TOC plugin, reducing knowledge base bounce rate by \textbf{42\%} by improving navigation speed and information findability.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches in \textbf{CI/CD} pipelines, reducing build and deployment failures by \textbf{80\%} through version pinning and automated regression checks.}
        \resumeItem{Elevated \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} across \textbf{WordPress} sites by optimizing assets, ARIA labels, and lazy loading.}
        \resumeItem{Built an internal microsite with \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee engagement by \textbf{50\%} by enabling modular content reuse across departments.}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{Spring Boot} and \textbf{React} platform serving \textbf{500+ users} with sub-\textbf{200ms} sync by implementing \textbf{WebSockets}, connection pooling, and efficient state management.}
        \resumeItem{Secured microservices with \textbf{JWT} and role-based access, maintaining stable sessions across \textbf{500+} concurrent connections during timed consultations.}
        \resumeItem{Designed modular \textbf{Spring Boot} APIs with \textbf{60+} endpoints and \textbf{PostgreSQL}, supporting reproducible releases via \textbf{Docker} on \textbf{Render} and \textbf{Vercel}.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Architected modular \textbf{n8n} pipeline, delivering validated resumes in \textbf{30 seconds} from a \textbf{Slack} trigger by orchestrating \textbf{OpenAI GPT}, transformations, and strict LaTeX validation.}
    \resumeItem{Implemented multi-level LaTeX validation, achieving \textbf{0} pipeline failures by rejecting malformed outputs and auto-reverting to verified templates before \textbf{GitHub} commits.}
    \resumeItem{Automated \textbf{100\%} of resume tailoring by integrating \textbf{HTTP} nodes, metadata normalization, and \textbf{GitHub} REST commits, enabling reproducible, version-controlled artifacts from a single event.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}