\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=cheil\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Accelerated product sourcing by \textbf{10-20} hours/week by architecting full-stack \textbf{React}+\textbf{Go} platform with real-time analysis across marketplaces.}
        \resumeItem{Scaled concurrent scraping to \textbf{500+} products/hour per marketplace by building \textbf{Go} microservices with rate limiting, retries, and anti-bot detection for reliability.}
        \resumeItem{Reduced manual validation time by \textbf{80\%} by developing \textbf{OpenAI} \textbf{GPT-3.5} profit analysis to normalize packs and flag marketplace mismatches.}
        \resumeItem{Achieved \textbf{99.9\%} uptime by deploying \textbf{Firebase Functions} and containerized \textbf{Go} services on \textbf{Google Cloud} with autoscaling, monitoring, and alerting.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Reduced bounce rate by \textbf{42\%} on knowledge bases by building a reusable Table of Contents \textbf{WordPress} plugin using \textbf{JavaScript}/\textbf{jQuery}.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} by fixing audits, standardizing \textbf{SEO} structure, and optimizing assets.}
        \resumeItem{Increased employee participation by \textbf{50\%} by delivering an internal microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, enabling modular content reuse across departments.}
        \resumeItem{Cut \textbf{CI/CD} build failures by \textbf{80\%} by resolving \textbf{Node.js} version mismatches and pipeline configs, stabilizing deployments across environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Supported \textbf{500+} users and \textbf{200+} concurrent sessions by building a \textbf{React}+\textbf{Spring Boot} platform with real-time \textbf{WebSockets} for PLAB 2 practice.}
        \resumeItem{Reduced sync latency to under \textbf{200ms} by implementing \textbf{STOMP} \textbf{WebSockets}, debounced events, and efficient client state management across roles.}
        \resumeItem{Shipped \textbf{60+} \textbf{REST} endpoints secured with \textbf{JWT}, backed by \textbf{PostgreSQL} and \textbf{Docker}, improving reliability in production deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Prep Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered AI interview generation with \textbf{Gemini} on \textbf{React}+\textbf{Node.js}, enabling tailored questions and explanations to streamline candidate practice sessions.}
        \resumeItem{Implemented \textbf{JWT}+\textbf{Google OAuth} with bcrypt and modal-based password reset, strengthening authentication and protecting routes end-to-end.}
        \resumeItem{Enabled reliable releases by integrating \textbf{CI/CD}, containerized configs, and tests, improving deployment consistency across environments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Frontend}}{React, Next.js, TypeScript, JavaScript (ES6+), TailwindCSS, HTML5, CSS3/Sass, Responsive \& Accessible Design (WCAG)}
    \resumeItem{\textbf{Backend \& DevOps}}{Node.js, Express, PostgreSQL, REST APIs, Docker, GitHub Actions, CI/CD, Google Cloud (GCP)}
    \resumeItem{\textbf{Tools \& Collaboration}}{Figma, WordPress (Custom Themes \& Plugins), SEO \& Lighthouse Optimization, Agile/Scrum, Git, Jest Testing}
  \resumeItemListEnd
%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}
