\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Automated containerized deployments with \textbf{Docker} and \textbf{GitHub Actions} to \textbf{Google Cloud Run}, cutting release time by \textbf{60\%} and sustaining \textbf{99.9\%} uptime.}
        \resumeItem{Scripted job orchestration and health checks in \textbf{Bash} and \textbf{Python}, reducing failed runs by \textbf{40\%} across concurrent \textbf{Go} microservices.}
        \resumeItem{Hardened \textbf{CI/CD} with secrets management, linting, and automated tests, preventing config drift and reducing rollback incidents by \textbf{50\%}.}
        \resumeItem{Standardized \textbf{Git}/\textbf{GitHub} branching and review gates, cutting merge conflicts by \textbf{45\%} and accelerating deployments.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Resolved Node.js environment mismatches in \textbf{CI/CD}, reducing build failures by \textbf{80\%} via version pinning and cache strategy in \textbf{GitHub Actions}.}
        \resumeItem{Wrote \textbf{Bash} scripts to standardize local WordPress setup and deployment steps, cutting onboarding time by \textbf{50\%} on \textbf{Linux}/macOS.}
        \resumeItem{Managed source control with \textbf{Git}/\textbf{GitHub}, enforcing branch policies and PR checks, reducing merge conflicts by \textbf{35\%}.}
        \resumeItem{Elevated Lighthouse performance/accessibility to \textbf{90+}/100 by optimizing assets and \textbf{HTTP} caching headers, improving load times by \textbf{40\%}.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Containerized backend and frontend with \textbf{Docker} and automated \textbf{CI/CD} via \textbf{GitHub Actions}, reducing deployment time by \textbf{55\%} and ensuring environment parity.}
        \resumeItem{Delivered sub-\textbf{200ms} real-time sync for \textbf{500+ users} by optimizing \textbf{WebSocket}/\textbf{HTTP} settings on \textbf{Linux} hosts.}
        \resumeItem{Deployed on \textbf{Render}/\textbf{Vercel} with HTTPS and DNS, achieving \textbf{99.9\%} uptime under production workloads.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{CI/CD} with \textbf{GitHub Actions} and \textbf{Docker}, reducing deployment time by \textbf{70\%} and enabling fast rollbacks.}
        \resumeItem{Authored YAML workflows with caching, tests, and build stages, increasing pipeline reliability by \textbf{90\%} and consistency across branches.}
        \resumeItem{Instrumented structured logs and health endpoints, shrinking MTTR by \textbf{35\%} during incidents and speeding \textbf{CD} validation.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: Python, Bash, JavaScript (ES6+), TypeScript, Go, SQL}
    \resumeItem{Frameworks \& Tools: Docker, GitHub Actions, Git, React, Node.js, Express, Spring Boot, PostgreSQL, Linux, Firebase/Firestore}
    \resumeItem{Other: DevOps, CI/CD, Containers, Linux (CLI), Shell scripting, YAML, Networking (HTTP/DNS), REST APIs, Google Cloud Platform, Render, Vercel, Supabase, Agile/Scrum}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}