\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Accelerated analytics responses by \textbf{70\%} in throughput-critical pipelines by optimizing \textbf{Firestore} indexing, async \textbf{Node.js}/\textbf{Go} \textbf{APIs}, and indexed pagination.}
        \resumeItem{Built reusable \textbf{React}/\textbf{TypeScript} components for real-time dashboards, sustaining \textbf{<350ms} interactions under heavy client-server traffic via debounced queries and memoized state.}
        \resumeItem{Scaled data ingestion to \textbf{1000+ records/hour} by engineering concurrent \textbf{Go} microservices with rate limiting, retries, and anti-bot handling.}
        \resumeItem{Achieved \textbf{99.9\%} uptime by deploying \textbf{Docker} services to \textbf{Google Cloud Run} and \textbf{Firebase Functions}, enabling automated scaling and fault isolation.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Improved navigation speed and cut bounce rate by \textbf{42\%} by building a reusable \textbf{JavaScript}/\textbf{jQuery} TOC plugin integrated into enterprise \textbf{WordPress} knowledge bases.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility scores to \textbf{90+} by fixing audit findings, optimizing assets, and standardizing \textbf{SEO} semantics across WordPress-based systems.}
        \resumeItem{Reduced \textbf{Node.js} \textbf{CI/CD} build failures by \textbf{80\%} by resolving environment mismatches, pinning dependencies, and introducing regression checks during Agile sprints.}
        \resumeItem{Boosted employee participation by \textbf{50\%} by delivering a modular \textbf{PHP} microsite integrating \textbf{REST APIs} and \textbf{Bootstrap}, enabling reusable content blocks across departments.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Served \textbf{500+ users} with sub-\textbf{200ms} real-time sync by building \textbf{React}/\textbf{TypeScript} frontend and \textbf{Spring Boot} backend using \textbf{WebSockets} and debounced state.}
        \resumeItem{Designed \textbf{60+} \textbf{REST APIs} in \textbf{Spring Boot} with \textbf{PostgreSQL} and \textbf{Flyway}, enabling role-based access and reliable session control with \textbf{JWT}.}
        \resumeItem{Reduced manual server setup to \textbf{0} by containerizing with \textbf{Docker} and deploying on \textbf{Render}/\textbf{Vercel}, sustaining stable performance under concurrent load.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Delivered validated resumes in \textbf{30 seconds} per request by orchestrating \textbf{n8n} nodes for \textbf{Slack} trigger, data fetch, \textbf{OpenAI GPT} inference, transformations, and atomic \textbf{GitHub} commits.}
    \resumeItem{Maintained \textbf{0} pipeline failures by enforcing multi-level \textbf{LaTeX} validation and conditional fallbacks, ensuring compile-safe outputs across all runs.}
    \resumeItem{Standardized X-Y-Z achievements across a \textbf{6-stage} workflow by templating prompts, validating symbols, and persisting artifacts through \textbf{GitHub REST API}.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}