\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered full-stack \textbf{React}+\textbf{Go} SaaS for real-time analytics, boosting data throughput by \textbf{35\%} via concurrent workers, \textbf{REST} APIs, and caching.}
        \resumeItem{Engineered modular \textbf{Go} microservices with idempotency, retries, and structured error handling, reducing failed API calls by \textbf{40\%} and improving reliability under burst traffic.}
        \resumeItem{Implemented secure authentication, CORS, and rate limiting across \textbf{REST} services, achieving \textbf{99.9\%} uptime with \textbf{Docker} deployments and \textbf{GitHub Actions} \textbf{CI/CD}.}
        \resumeItem{Optimized \textbf{NoSQL} \textbf{Firestore} queries with indexed pagination and caching, improving retrieval speed by \textbf{70\%} on datasets exceeding \textbf{10,000} products.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{JavaScript}/\textbf{jQuery} navigation components for \textbf{WordPress}, improving knowledge-base navigation speed and lowering bounce rate by \textbf{42\%}.}
        \resumeItem{Increased Lighthouse performance and accessibility scores to \textbf{90+} by optimizing \textbf{HTML}, \textbf{CSS}, images, and deferred scripts.}
        \resumeItem{Delivered internal microsite using \textbf{PHP} and \textbf{REST} integrations, boosting employee engagement by \textbf{50\%} and enabling modular content reuse.}
        \resumeItem{Resolved Node.js environment mismatches in \textbf{CI/CD}, reducing build failures by \textbf{80\%} and improving deployment reliability with \textbf{Git} version control.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{Java} \textbf{Spring Boot} \textbf{REST} APIs using \textbf{OOP} patterns and global \textbf{exception handling}, reducing errors by \textbf{45\%} across \textbf{60+} endpoints.}
        \resumeItem{Delivered real-time sessions via \textbf{WebSocket} (\textbf{STOMP}) with \textbf{React}, sustaining \textbf{500+ users} under \textbf{200ms} latency.}
        \resumeItem{Secured \textbf{JWT} authentication and optimized \textbf{PostgreSQL} with indexes; containerized with \textbf{Docker}, improving throughput by \textbf{40\%} and deployment consistency.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Built \textbf{REST}ful APIs in \textbf{Node.js}/\textbf{Express} with \textbf{JWT} and \textbf{Google OAuth}, reducing auth errors by \textbf{60\%}.}
        \resumeItem{Designed \textbf{MongoDB} schemas and indexes, accelerating queries by \textbf{50\%} and scaling to \textbf{5K+} records with consistent response times.}
        \resumeItem{Automated testing and deployments with \textbf{GitHub Actions} and \textbf{Docker}, cutting release time by \textbf{70\%} and improving reliability.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: Java, JavaScript (ES6+), TypeScript, Go, Python, SQL, HTML5, CSS3}
    \resumeItem{Frameworks \& Tools: Spring Boot, React, Node.js, Express, Docker, PostgreSQL, MongoDB, WebSocket, Git, GitHub Actions}
    \resumeItem{Other: REST APIs, OOP, Exception Handling, Agile/Scrum, CI/CD, WordPress (Custom Plugins), Figma, SEO Optimization}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}