\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built scalable \textbf{React} UI delivering \textbf{350ms} debounced searches for arbitrage dashboards by implementing \textbf{Redux-Saga}, virtualized lists, and dynamic filters \textbf{20+} to streamline analysis.}
        \resumeItem{Accelerated data retrieval by \textbf{70\%} on \textbf{Firestore} datasets \textbf{10,000+} by adding indexed pagination, batched reads, and lazy loading across \textbf{Go}/\textbf{Node.js} APIs.}
        \resumeItem{Processed \textbf{500+} products/hour per marketplace with resilient \textbf{Go} scrapers by implementing rate limiting, retries, and anti-bot detection, reducing manual checks by \textbf{80\%}.}
        \resumeItem{Deployed \textbf{Docker}-containerized \textbf{Go} services on \textbf{GCP} with \textbf{CI/CD} via \textbf{GitHub Actions}, achieving \textbf{99.9\%} uptime and streamlining releases by automating rollouts, monitoring, and alerts.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{JavaScript}/\textbf{jQuery} TOC plugin improving navigation speed by \textbf{42\%} on enterprise knowledge bases by modularizing anchors, deep links, and scroll-spy behaviors.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility to \textbf{90+} across \textbf{WordPress} sites by fixing images, ARIA labels, and caching, boosting SEO and user engagement.}
        \resumeItem{Reduced \textbf{Node.js} \textbf{CI/CD} build failures by \textbf{80\%} in multi-environment pipelines by standardizing versions, lockfiles, and regression checks using \textbf{Jira}-tracked sprints.}
        \resumeItem{Increased participation by \textbf{50\%} across departments by building modular \textbf{PHP}+\textbf{Bootstrap} microsite components integrating \textbf{REST APIs} and reusable content blocks.}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered real-time \textbf{React}+\textbf{Spring Boot} platform serving \textbf{500+ users} with sub-\textbf{200ms} sync by implementing \textbf{WebSockets} and optimized state management.}
        \resumeItem{Maintained sub-\textbf{200ms} latency under peak usage by implementing \textbf{JWT}-secured microservices, \textbf{PostgreSQL} indexing, and \textbf{Docker}-based deployments.}
        \resumeItem{Shipped \textbf{60+} \textbf{REST APIs} by designing modular \textbf{Spring Boot} services and tests, accelerating delivery across iterations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Automated end-to-end tailoring in \textbf{n8n}, delivering validated outputs to \textbf{GitHub} within \textbf{30 seconds} from \textbf{Slack} trigger by orchestrating retrieval, transformation, and \textbf{OpenAI} inference.}
    \resumeItem{Ensured \textbf{0} invalid documents in production by implementing multi-level \LaTeX validation, tag balancing, and symbol escaping, gating commits through authenticated \textbf{GitHub Actions}.}
    \resumeItem{Achieved \textbf{0} pipeline failures under concurrent runs by adding conditional fallbacks and state propagation, producing deterministic, reproducible artifacts.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}