\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Optimized \textbf{Firestore} indexing and asynchronous \textbf{API} batching for analytics pipelines, cutting latency by \textbf{70\%} by profiling queries and implementing indexed pagination.}
        \resumeItem{Delivered reusable \textbf{React} components for real-time dashboards, sustaining sub-\textbf{350ms} interactions under heavy traffic by memoizing state, virtualizing lists, and debouncing network calls.}
        \resumeItem{Scaled \textbf{Go} microservices to process \textbf{1000+} records/hour reliably by parallelizing scrapers with rate limiting and retries, increasing marketplace data coverage by \textbf{2.5x}.}
        \resumeItem{Shipped scalable \textbf{Node.js} services on \textbf{GCP} with \textbf{Docker} and monitoring, achieving \textbf{99.9\%} uptime by automating health checks, autoscaling policies, and alerting.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript}/\textbf{jQuery} TOC plugin for enterprise \textbf{WordPress}, reducing knowledge-base bounce rate by \textbf{42\%} by accelerating in-page navigation and deep-linking.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility to \textbf{90+} across internal sites by fixing \textbf{SEO} issues, optimizing images, and deferring scripts within \textbf{PHP}/\textbf{Node.js} \textbf{CI} workflows.}
        \resumeItem{Delivered \textbf{PHP} microsite integrating \textbf{REST APIs} and \textbf{Bootstrap}, increasing employee participation by \textbf{50\%} by modularizing content blocks and simplifying submissions.}
        \resumeItem{Reduced \textbf{Node.js} \textbf{CI/CD} failures by \textbf{80\%} in shared pipeline by standardizing versions, pinning dependencies, and adding regression checks during \textbf{Agile} sprints.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered \textbf{React}/\textbf{Spring Boot} platform for \textbf{500+ users}, sustaining sub-\textbf{200ms} real-time sync via \textbf{WebSockets} by optimizing message batching, backpressure, and connection reuse.}
        \resumeItem{Delivered \textbf{60+} \textbf{REST APIs} for role-based sessions by modularizing \textbf{Spring Boot} services and enforcing \textbf{JWT} scopes to streamline auth flows.}
        \resumeItem{Deployed on \textbf{Render}/\textbf{Vercel} with \textbf{Docker} and \textbf{PostgreSQL}, improving cold-starts to under \textbf{500ms} by connection pooling and health checks.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Automated resume tailoring pipeline in \textbf{n8n}, generating validated \textbf{LaTeX} resumes in under \textbf{30s} per request by orchestrating \textbf{Slack} triggers, \textbf{OpenAI} inference, and \textbf{GitHub} commits.}
    \resumeItem{Achieved \textbf{100\%} document integrity in production by enforcing multi-level \textbf{LaTeX} validation, escaping, and structure checks before atomic \textbf{GitHub} writes.}
    \resumeItem{Reduced manual edits by \textbf{80\%} by generating quantified X-Y-Z bullets with \textbf{OpenAI} and codifying schema transformations in \textbf{JavaScript} nodes.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}