\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Delivered responsive \textbf{React}+\textbf{TypeScript} UI using \textbf{Redux-Saga}, achieving query latency \textbf{<350ms} over \textbf{10k+} items by implementing debounced filters and \textbf{Firestore} indexing, accelerating product sourcing.}
        \resumeItem{Built scalable \textbf{Go} microservices with rate limiting, \textbf{retry} logic, and \textbf{caching}, reducing failed \textbf{API} calls by \textbf{40\%} during multi-marketplace scraping and improving reliability under burst traffic.}
        \resumeItem{Integrated \textbf{OpenAI} into profit analysis, normalizing pack quantities and flagging inconsistencies, cutting manual validation by \textbf{80\%} across marketplaces and accelerating product matching.}
        \resumeItem{Established reusable \textbf{React} component patterns and review checklists, increasing frontend delivery velocity by \textbf{20\%} and maintainability while mentoring peers in \textbf{Agile} sprints.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{JavaScript}/\textbf{jQuery} TOC plugin for \textbf{WordPress} knowledge bases, reducing bounce rate by \textbf{42\%} by auto-generating anchors and smooth-scrolling, accelerating in-page navigation.}
        \resumeItem{Raised \textbf{Lighthouse} performance and accessibility to \textbf{90+} by optimizing \textbf{SEO} structure, deferring scripts, compressing images, and fixing \textbf{ARIA}/contrast issues across marketing pages.}
        \resumeItem{Delivered an internal microsite with \textbf{PHP}, \textbf{REST APIs}, and \textbf{Bootstrap}, increasing employee participation by \textbf{50\%} through modular content blocks and responsive components.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches in \textbf{CI/CD}, reducing build and deployment failures by \textbf{80\%} and stabilizing multi-environment releases.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time \textbf{React}+\textbf{Spring Boot} platform with \textbf{WebSockets}, serving \textbf{500+} users by enabling role-based sessions, timers, and feedback workflows for PLAB2 practice.}
        \resumeItem{Reduced real-time sync latency to \textbf{<200ms} by optimizing message handlers, batching updates, and refining session state, improving collaboration quality during consultations.}
        \resumeItem{Hardened \textbf{REST APIs} with \textbf{JWT}, and containerized with \textbf{Docker} on cloud hosting, improving deployment reliability and enabling zero-downtime updates.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Implemented \textbf{Gemini AI} to generate personalized questions, delivering \textbf{<1s} prompts in \textbf{React} mock sessions by streaming responses and caching frequent queries.}
        \resumeItem{Secured authentication with \textbf{Google OAuth}, \textbf{JWT}, and \textbf{bcrypt} email resets, reducing account recovery time by \textbf{70\%} and improving signup conversion.}
        \resumeItem{Automated \textbf{testing} and \textbf{CI/CD} with \textbf{GitHub Actions} and \textbf{Docker}, increasing deployment frequency by \textbf{3x} while keeping releases stable.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages:} JavaScript (ES6+), TypeScript, Go, Python, SQL}
    \resumeItem{\textbf{Frameworks \& Tools:} React, Node.js, Express, Spring Boot, Docker, PostgreSQL, GitHub Actions}
    \resumeItem{\textbf{Other:} WordPress (Custom Plugins), REST APIs, Agile/Scrum, Figma, SEO Optimization, CI/CD}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}