\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack SaaS, enabled users discover profitable products \textbf{10--20 hrs/week faster} using \textbf{React}, \textbf{Go}, \textbf{Firebase}.}
        \resumeItem{Built high-performance \textbf{Go} microservices scraping \textbf{500+ products/hour} per marketplace with rate limiting and retries, improving reliability by \textbf{40\%}.}
        \resumeItem{Reduced manual validation time by \textbf{80\%} using AI normalization and server checks with \textbf{OpenAI} and backend heuristics.}
        \resumeItem{Optimized \textbf{Firestore} queries and containerized services on \textbf{GCP}, improving retrieval speed by \textbf{70\%} and achieving \textbf{99.9\%} uptime.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable TOC plugin, improving navigation speed and reducing bounce rate by \textbf{42\%} using \textbf{WordPress}, \textbf{PHP}, \textbf{JavaScript}.}
        \resumeItem{Raised Lighthouse performance and accessibility scores to \textbf{90+} by optimizing assets and SEO using \textbf{JavaScript} and \textbf{PHP}.}
        \resumeItem{Built internal microsite that increased employee participation by \textbf{50\%} using \textbf{PHP}, \textbf{Bootstrap}, and REST APIs.}
        \resumeItem{Resolved Node.js CI/CD environment issues, cutting build failures by \textbf{80\%} and improving deployment reliability via \textbf{CI/CD} fixes.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time platform for \textbf{500+} users with \textbf{React} and \textbf{Spring Boot}, enabling role-based sessions via \textbf{WebSockets}.}
        \resumeItem{Reduced sync latency to under \textbf{200ms} through optimized message handling and session logic using \textbf{STOMP} and WebSocket tuning.}
        \resumeItem{Dockerized and deployed with \textbf{PostgreSQL}, improving scalability and supporting indexed pagination and migrations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Integrated \textbf{Gemini AI} to generate personalized interview scenarios, reducing manual content creation time by \textbf{90\%}.}
        \resumeItem{Implemented secure auth with \textbf{Google OAuth} and \textbf{JWT}, improving onboarding and account recovery flows.}
        \resumeItem{Enabled CI/CD with \textbf{GitHub Actions} and automated testing to accelerate stable deployments.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: Go, TypeScript, JavaScript (ES6+), Python, SQL, Java, PHP, C\#.}
    \resumeItem{Frameworks \& Platforms: React, Node.js, Express, Spring Boot, Firebase / Firestore, PostgreSQL, Docker, GCP (Cloud Run), Vercel, Render.}
    \resumeItem{Data \& DevOps: REST APIs, CI/CD (GitHub Actions), Docker, IaC concepts, monitoring, BigQuery (familiar), authentication patterns (JWT, OAuth).}
    \resumeItem{Other: Agile/Scrum, WebSockets, OpenAI APIs, SEO, Lighthouse, Figma, unit testing, code review practices.}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}