\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{React} components and optimized \textbf{Node.js}/\textbf{Go} \textbf{REST APIs}, reducing dashboard response times by \textbf{35\%} for internal tools by profiling bottlenecks and introducing result caching.}
        \resumeItem{Accelerated \textbf{Firestore} retrieval by \textbf{70\%} on \textbf{10,000+} records by implementing indexed pagination and lazy loading across \textbf{Firebase Functions} and \textbf{React} clients.}
        \resumeItem{Scaled concurrent ingestion to \textbf{500+} products/hour using \textbf{Go} microservices with rate limiting and retries on \textbf{GCP}, achieving \textbf{99.9\%} uptime for sourcing pipelines.}
        \resumeItem{Integrated \textbf{Amazon SP-API}, \textbf{Keepa}, and \textbf{Stripe}, reaching \textbf{95\%+} profit-calculation accuracy by unifying pricing data and reducing manual validation by \textbf{80\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable \textbf{JavaScript}/\textbf{jQuery} TOC plugin for \textbf{WordPress} knowledge bases, reducing bounce rate by \textbf{42\%} by accelerating in-page navigation and standardizing headings.}
        \resumeItem{Resolved \textbf{Node.js} environment mismatches in \textbf{CI/CD}, cutting build failures by \textbf{80\%} by standardizing \textbf{NVM} versions and adding regression checks in shared pipelines.}
        \resumeItem{Elevated \textbf{Lighthouse} performance and accessibility to \textbf{90+} by fixing \textbf{SEO} metadata, implementing lazy loading, and refining \textbf{ARIA} semantics across WordPress sites.}
        \resumeItem{Built an engagement microsite with \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing employee participation by \textbf{50\%} by modularizing content and enabling department-level reuse.}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built full-stack platform with \textbf{React} and \textbf{Spring Boot}, supporting \textbf{500+} users with sub-\textbf{200ms} \textbf{WebSockets} sync by optimizing state handling and connection pooling.}
        \resumeItem{Secured sessions with \textbf{JWT} and RBAC in \textbf{Spring Security}, reducing auth errors by \textbf{60\%} under load by adding token refresh and server-side validation.}
        \resumeItem{Automated deployments with \textbf{Docker}, \textbf{PostgreSQL}, and \textbf{CI/CD} on \textbf{Render}/\textbf{Vercel}, cutting release time by \textbf{70\%} by automating tests and database migrations.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Orchestrated \textbf{n8n} pipeline integrating \textbf{Slack}, \textbf{OpenAI}, and \textbf{GitHub REST API}, generating validated \textbf{LaTeX} resumes in \textbf{30 seconds} by chaining trigger, transform, inference, and validation nodes.}
    \resumeItem{Achieved \textbf{0} failures by adding multi-level \textbf{LaTeX} validation and conditional fallbacks, eliminating invalid outputs by \textbf{100\%} through structure checks, escaping, and tag balance before commit.}
    \resumeItem{Reduced manual tailoring by \textbf{80\%} by automating versioned commits via \textbf{GitHub API} and \textbf{CI/CD}, improving reproducibility and traceability across resume updates.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}