\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com?utm_source=osi\&utm_medium=resume}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://arbithub.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Architected full-stack SaaS using \textbf{React}, \textbf{TypeScript}, and \textbf{Node.js}/\textbf{Express}, saving users \textbf{10-20 hours/week} via automated sourcing, dashboards, and analytics.}
        \resumeItem{Built concurrent \textbf{Go} services with rate limiting, retries, and caching, increasing data throughput \textbf{35\%} and reducing failed API calls \textbf{40\%} across marketplaces.}
        \resumeItem{Implemented \textbf{Stripe} payments and secure auth on \textbf{Firebase}, achieving \textbf{99.9\%} uptime with \textbf{CI/CD} automation and API \textbf{CORS}/\textbf{rate limiting}.}
        \resumeItem{Delivered responsive dashboards with \textbf{React}, \textbf{Tailwind CSS}, and indexed queries, keeping interactions under \textbf{350ms} and scaling to \textbf{10K+} products.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Web Developer, Co-op}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Developed reusable WordPress components in \textbf{PHP} and \textbf{JavaScript}, improving navigation and reducing bounce rate \textbf{42\%} across enterprise knowledge bases.}
        \resumeItem{Optimized SEO, accessibility, and performance, lifting \textbf{Lighthouse} scores to \textbf{90+} via semantic \textbf{HTML5}, deferred scripts, and image compression.}
        \resumeItem{Resolved \textbf{Node.js} environment issues in \textbf{CI/CD}, cutting build failures \textbf{80\%} and stabilizing deployments with \textbf{Git}/\textbf{GitHub} workflows.}
        \resumeItem{Launched an internal microsite consuming \textbf{REST} APIs with \textbf{Bootstrap}, boosting employee engagement \textbf{50\%} through responsive \textbf{HTML5}/\textbf{CSS3} and Agile collaboration.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time platform for \textbf{500+} users using \textbf{React}, \textbf{TypeScript}, \textbf{Spring Boot}, and \textbf{WebSocket}, enabling live role-play, timed cases, and feedback workflows.}
        \resumeItem{Reduced sync latency under \textbf{200ms} by optimizing message routing and session state; secured REST endpoints with \textbf{JWT} and \textbf{Spring Security}.}
        \resumeItem{Containerized services with \textbf{Docker} and provisioned \textbf{PostgreSQL} migrations, increasing scalability and reliability during peak traffic.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{AI-Powered Interview App}}{\href{https://interviewcoach-ai.vercel.app}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {Full-Stack Interview Preparation Tool}{}
      \resumeItemListStart
        \resumeItem{Delivered MERN app with \textbf{MongoDB}, \textbf{Express}, \textbf{React}, \textbf{Node.js}, using \textbf{Gemini AI} to generate tailored interviews and practice sessions.}
        \resumeItem{Implemented authentication with \textbf{JWT} and \textbf{Google OAuth}, enforcing role-based guards and achieving \textbf{100\%} protected API coverage.}
        \resumeItem{Built responsive UI with \textbf{Tailwind CSS} and enabled continuous delivery via \textbf{CI/CD} on \textbf{GitHub Actions}, eliminating manual deploy steps on main.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{Languages: JavaScript (ES6+), TypeScript, Go, Java, PHP, Python, SQL}
    \resumeItem{Frameworks \& Tools: React, Node.js, Express, Redux, Tailwind CSS, Spring Boot, Docker, MongoDB, PostgreSQL, MySQL, Firebase, GitHub Actions, Stripe API}
    \resumeItem{Other: REST APIs, HTML5, CSS3, CI/CD, Git, GitHub, Agile/Scrum, WordPress (Custom Plugins), SEO Optimization, Figma, Google Cloud Platform, Vercel, Render}
  \resumeItemListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Diploma in Web Development and Internet Applications; Dean's Honour List, \textbf{GPA: 3.77}}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}