\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Launched full-stack \textbf{SaaS platform} enabling real-time arbitrage, reducing product research time by \textbf{10--20 hours/week} across leading e-commerce marketplaces.}
        \resumeItem{Built scalable \textbf{Go} microservices to scrape \textbf{500+ products/hour} using retry logic and rate-limiting for reliable concurrent executions.}
        \resumeItem{Engineered dynamic dashboards using \textbf{React}, \textbf{Redux}, and export features with \textbf{20+ filters} supporting sub-\textbf{350ms} interactive search.}
        \resumeItem{Optimized \textbf{Firestore} pagination via indexed queries and lazy loading, improving data fetch speed by \textbf{70\%}.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} component for enterprise CMS, improving site navigation and lowering bounce rates by \textbf{42\%}.}
        \resumeItem{Fixed \textbf{Node.js CI/CD} conflicts across pipelines, cutting deployment failures by \textbf{80\%} within Agile release cycles.}
        \resumeItem{Created internal microsite with \textbf{PHP} and \textbf{Bootstrap} to boost employee engagement by \textbf{50\%} through reusable content modules.}
        \resumeItem{Raised \textbf{Lighthouse} SEO/accessibility scores above \textbf{90+} on WordPress assets by implementing audit-driven code updates.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built secure \textbf{Spring Boot + React} platform with \textbf{JWT} and WebSocket support, handling \textbf{500+ active users} under \textbf{200ms} latency.}
        \resumeItem{Designed \textbf{60+ RESTful} microservice endpoints deployed via \textbf{Docker}, \textbf{PostgreSQL}, and \textbf{Flyway} for robust versioning.}
        \resumeItem{Implemented role-based sessions, chat, and live feedback using \textbf{STOMP} and \textbf{Tailwind CSS} for PLAB2 candidates.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app/}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {AI Interview Preparation Platform}{}
      \resumeItemListStart
        \resumeItem{Developed \textbf{MERN} stack platform integrating \textbf{Gemini AI} to generate tailored interview questions, explanations, and persistent tracking notes.}
        \resumeItem{Implemented \textbf{Google OAuth}, \textbf{JWT}, and reset flows to enhance secure login and streamline \textbf{user experience}.}
        \resumeItem{Built accessible, responsive UI using \textbf{TailwindCSS} and \textbf{Framer Motion}, ensuring WCAG compliance across devices.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}