\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Built reusable \textbf{React} UI and optimized \textbf{Node.js}/\textbf{Go} \textbf{APIs}, cutting catalog fetch latency by \textbf{70\%} in production by implementing indexed queries, caching, and async pipelines.}
        \resumeItem{Integrated \textbf{GA4}, \textbf{Facebook Pixel}, \textbf{TikTok Pixel}, measuring \textbf{8+} conversion events and increasing trials-to-subscriptions by \textbf{25\%} via A/B experiments and UX refinements.}
        \resumeItem{Deployed scalable backend on \textbf{Firebase Functions} and \textbf{Google Cloud}, achieving \textbf{99.9\%} uptime by configuring health checks, autoscaling policies, and error monitoring.}
        \resumeItem{Ensured secure, compliant flows by implementing \textbf{Stripe} \textbf{PCI}-aligned webhooks, \textbf{CORS} whitelisting, and rate limiting, reducing payment failures by \textbf{30\%} across \textbf{API} endpoints.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Published and optimized \textbf{WordPress} content, raising \textbf{Lighthouse} performance and accessibility to \textbf{90+} by fixing \textbf{HTML}/\textbf{CSS}/\textbf{JavaScript} issues and compressing assets across templates.}
        \resumeItem{Built reusable \textbf{JavaScript}/\textbf{jQuery} Table of Contents plugin, reducing bounce rate by \textbf{42\%} on knowledge bases by improving in-page navigation and anchor link accuracy.}
        \resumeItem{Launched an internal microsite with \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing employee participation by \textbf{50\%} through modular content components and event-driven forms.}
        \resumeItem{Reduced \textbf{Node.js} \textbf{CI/CD} build failures by \textbf{80\%} by resolving environment mismatches and adding regression checks, improving release reliability across shared \textbf{Git} workflows.}
        
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Delivered a \textbf{React} + \textbf{Spring Boot} platform for \textbf{500+} users, sustaining sub-\textbf{200ms} sync via \textbf{WebSocket} events and efficient state updates.}
        \resumeItem{Exposed \textbf{60+} \textbf{REST APIs} for role workflows by implementing \textbf{JWT}-secured microservices with \textbf{Spring Security}, stabilizing sessions under load.}
        \resumeItem{Deployed with \textbf{Docker}, \textbf{PostgreSQL}, and \textbf{CI/CD} to \textbf{Render}/\textbf{Vercel}, enabling predictable releases and maintaining uptime for \textbf{500+} active users.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Resume Tailoring Automation Workflow}}{\href{https://github.com/altansaid/resume-automation-workflow}{GitHub}}
      {AI-Powered Resume Optimization System}{}
      \resumeItemListStart
    \resumeItem{Automated resume publishing with \textbf{n8n}, producing validated \textbf{LaTeX} from structured data and committing to \textbf{GitHub} within \textbf{30s} using multi-stage checks.}
    \resumeItem{Eliminated broken outputs by adding layered \textbf{LaTeX} validation, cutting formatting errors by \textbf{100\%} pre-commit through tag, encoding, and escape verification.}
    \resumeItem{Delivered version-controlled resumes via \textbf{Slack}-triggered jobs, reducing manual publishing effort by \textbf{90\%} by automating transforms and persistence.}



      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}