\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADER----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Said Altan} & \href{mailto:altansaid13@outlook.com}{altansaid13@outlook.com} \\
  \href{https://saidaltan.com}{saidaltan.com} & (343) 988-3084 \\
  \href{https://www.linkedin.com/in/altansaid}{linkedin.com/in/altansaid} & \href{https://github.com/altansaid}{github.com/altansaid} \\
\end{tabular*}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://arbitragecyclops.com/}{Arbitrage Cyclops}}{Jul 2025 -- Present}
      {Software Developer}{Remote}
      \resumeItemListStart
        \resumeItem{Engineered \textbf{Go} microservices scraping \textbf{500+ products/hour} across marketplaces by implementing retry logic and \textbf{anti-bot detection} for scalable, fault-tolerant data extraction.}
        \resumeItem{Integrated \textbf{Amazon SP-API}, \textbf{Keepa}, and \textbf{Stripe}, enabling profit and ROI analysis with \textbf{95\%+} pricing accuracy across thousands of real-time API responses.}
        \resumeItem{Optimized \textbf{Firestore} queries via lazy loading and pagination, reducing lookup time by \textbf{70\%} on \textbf{10,000+ record} datasets in production analytics dashboard.}
        \resumeItem{Deployed containerized \textbf{Go} services using \textbf{Firebase Functions} on \textbf{Google Cloud}, sustaining \textbf{99.9\% uptime} under continuous production traffic.}
      \resumeItemListEnd

    \resumeSubheading
      {\href{https://solace.com}{Solace}}{Sep 2024 -- Dec 2024}
      {Full Stack Web Developer Intern}{Ottawa, ON}
      \resumeItemListStart
        \resumeItem{Delivered reusable \textbf{JavaScript/jQuery} navigation plugin that reduced enterprise platform bounce rates by \textbf{42\%} through hierarchical caching and smooth content transitions.}
        \resumeItem{Resolved \textbf{Node.js} CI/CD version conflicts by implementing tooling validation and semantic tracking, cutting deployment failures by \textbf{80\%}.}
        \resumeItem{Elevated accessibility and performance scores to \textbf{90+} across internal apps by remediating \textbf{Lighthouse} issues in structured metadata and semantic HTML.}
        \resumeItem{Developed modular internal microsite using \textbf{PHP}, \textbf{Bootstrap}, and \textbf{REST APIs}, increasing engagement metrics by \textbf{50\%} via dynamic content management.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\textbf{PLAB2 Practice Platform}}{\href{https://plab2practice.com}{Live Demo} | \href{https://github.com/altansaid/plab2projectnew}{GitHub}}
      {Real-time Collaborative Practice Platform}{}
      \resumeItemListStart
        \resumeItem{Built real-time web app with \textbf{React}, \textbf{Spring Boot}, and \textbf{WebSocket}, handling \textbf{500+ users} at sub-\textbf{200ms} latency through event-based state syncing.}
        \resumeItem{Developed \textbf{JWT}-secured microservices using \textbf{Spring Security} and \textbf{PostgreSQL}, ensuring reliable user authentication under concurrent test loads.}
        \resumeItem{Configured full \textbf{CI/CD} deployment by containerizing backend in \textbf{Docker} on \textbf{Render} and serving frontend on \textbf{Vercel} with zero-downtime updates.}
      \resumeItemListEnd

    \resumeSubheading
      {\textbf{Interview Coach AI}}{\href{https://interviewcoach-ai.vercel.app/}{Live Demo} | \href{https://github.com/altansaid/interviewcoach-ai}{GitHub}}
      {AI-Powered Interview Preparation Platform}{}
      \resumeItemListStart
        \resumeItem{Created \textbf{MERN}-based platform generating dynamic interview prompts using \textbf{Gemini API}, enabling AI-driven question sets tailored to role and experience level.}
        \resumeItem{Implemented secure user flows with \textbf{JWT} and \textbf{Google OAuth}, adding password reset and session validation for protected authentication.}
        \resumeItem{Enhanced user experience using \textbf{TailwindCSS} and \textbf{Framer Motion}, achieving responsive \& WCAG-compliant design across mobile and desktop views.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
  \resumeItemListStart
    \resumeItem{\textbf{Languages}}{Java, JavaScript, Python, TypeScript, Go, SQL, HTML, CSS}
    \resumeItem{\textbf{Frameworks \& Tools}}{Spring Boot, React, Node.js, REST APIs, Docker, Git, Firebase, GCP, PostgreSQL}
    \resumeItem{\textbf{Key Focus Areas}}{Scalability, Throughput Optimization, Client-Server Architecture, Testing \& Debugging, R\&D Prototyping}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {\href{https://www.algonquincollege.com/sat/program/web-development-internet-applications/}{Algonquin College of Applied Arts and Technology}}{Apr 2025}
      {Web Development and Internet Applications; Dean's Honour List, GPA: 3.77}{Ottawa, ON}
  \resumeSubHeadingListEnd

\end{document}